%
% This file is part of Calicut University Question Paper Collection.
%
% Copyright (c) 2012-2015 Mohammed Sadik P. K. <sadiq (at) sadiqpk (d0t) org>.
% License: GNU GPLv3 or later
%
% Calicut University Question Paper Collection is free software: you can
% redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation, either version 3 of the License, or
% (at your option) any later version.
% 
% Calicut University Question Paper Collection is distributed in the hope
% that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
% 
% You should have received a copy of the GNU General Public License
% along with Calicut University Question Paper Collection.
% If not, see <http://www.gnu.org/licenses/>.
% 
%

\def \subj{AI 09 405---ELECTRONICS CIRCUITS---II}

\mainhead{C 61594}{2}
\semfour{APRIL 2014}
\sub{\subj}
\maxtime

\partA

\iitem What is the role of commutating capacitors in multivibrator
  circuit?
\item Design a delay of 5ms using 555 timer.
\item Design an RC phase-shift oscillator fro frequency of operation
  of 4 kHz.
\item Define harmonic distortion in power amplifiers.
\item If the rise time of a transistor is 25 microseconds, determine
  its bandwidth.

\markA
\partB

\item Explain the response of RC high-pass filter to a square wave input.
\item Explain the principle of operation of miller sweep circuit.
\item With suitable circuit diagram explain about trasnconductance and
  current amplifiers.
\item Explain the advantages and disadvantages of tuned amplifiers.
\item Describe the operation of class A, class B, class C and class AB
  with the help of V--I curves.
\item Explain the working of unsymmetrical triggering circuit.

\markB
\partC

\item Discuss the working of astable multivibrator with suitable circuit
  and waveforms.
\Or
\item Describe the operation of CMOS inverter and response of RC low-pass
  filter to a ramp input.

\newpage \again

\item Explain the operation of current time base generator.
\Or
\item Explain the astable mode of operation of 555 timer.

\item Derive the expression for input and output resistance of current
  shunt feedback.
\Or
\item Derive the expression for the frequency of operation of Wien bridge
  and Colpitt's oscillator.

\item Explain the operation of class B push-pull amplifier and compare
  its performance with other amplifiers.
\Or
\item Explain the operation of stagger tuned circuit and biasing of
  class C amplifiers.

\ene
\markC

\newpage

\mainhead{C 26898}{2}
\semfour{MAY 2012}
\sub{\subj}
\maxtime

\partA

\iitem What are commutating capacitors?
\item Define sweep speed.
\item Draw the block diagram of a current shunt feedback amplifier.
\item Give the application of class A, class B and class C power amplifiers.
\item What is Barkhausen criterion?

\markA 
\partB

\item Explain the working of a MOS inverter?
\item Discuss the general features of time base signal. Draw the schematic diagrams
  of Miller and Bootstrap time base generators.
\item Discuss on the frequency stability of an oscillator.
\item Discuss the efficiency of class A, class B, class C and class AB amplifiers.
\item Explain the working of PLL.
\item Discuss effect of negative feedback on input impedance of a voltage shunt feedback circuit
  and current series feedback circuit.

\markB

\newpage \again

\partC

\item
\iitem Explain the working of a UJT sweep circuit
\Or
\item Explain the working of Schmitt trigger circuit.
\ene

\item 
\iitem Explain the working of 555 IC timer as a monostable multivibrator.
\Or
\item Explain any two applications of PLL.
\ene

\item
\iitem Explain the working of Wien bridge oscillator.
\Or
\item  Explain the working of a Hartley oscillator.
\ene

\item
\iitem Explain the working of transformer coupled class A power amplifier.
\Or
\item Explain the working of class C amplifiers.
\ene

\markC
\ene

\newpage

\mainhead{C 15658}{1}
\semfour{JUNE 2011}
\sub{\subj}
\maxtime

\partA

\iitem State any {\em two} applications of transistor as a switch.
\item What is a Miller circuit.
\item Classify feedback amplifiers.
\item What are harmonics?
\item What is a negative resistance device? Give an example.

\markA
\partB

\item Explain the need and use of commutating capacitors in a bistable multivibrator circuit.
\item Explain the working of a 555 timer IC.
\item \iitem What are the advantages of negative feedback?
\item What is the criteria for oscillation?
\ene
\item Explain the applications of various power amplifiers.
\item Explain the response of a high pass RC circuit to a step input.
\item State the general features of a time base generator.

\markB
\partC

\item \iitem Explain the working of a monostable multivibrator using transistors.
\Or
\item Explain the working of UJT sweep circuit.
\ene

\newpage \again

\item \iitem  Explain the working of a Bootstrap time base generator.
\Or
\item Explain any {\em two} applications of PLL.
\ene

\item \iitem Explain the working of a Hartley oscillator.
\Or
\item Explain the effect of feedback on voltage series, current series, voltage shunt and current
  shunt feedback.
\ene

\item \iitem Explain the working of class C amplifiers.
\Or
\item Explain the working of a class B push-pull amplifier.
\ene

\markC
\ene
