%
% This file is part of Calicut University Question Paper Collection.
%
% Copyright (c) 2012-2015 Mohammed Sadik P. K. <sadiq (at) sadiqpk (d0t) org>.
% License: GNU GPLv3 or later
%
% Calicut University Question Paper Collection is free software: you can
% redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation, either version 3 of the License, or
% (at your option) any later version.
% 
% Calicut University Question Paper Collection is distributed in the hope
% that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
% 
% You should have received a copy of the GNU General Public License
% along with Calicut University Question Paper Collection.
% If not, see <http://www.gnu.org/licenses/>.
% 
%
\def \subj{EN 09/ PTEN 09 401 B---Engineering Mathematics---IV}

\mainhead{C 40931}{2}
\semfour{APRIL 2013}
\sub {\subj}
\maxtime

\partA

\iitem If X follows the uniform distribution in (-K, K), find K such that
  P(X$>1 = \dfrac{1}{3}$.
\item Find the Z-transform of $n^2$.
\item Show that P$_\text{n}$(1) = 1.
\item Solve $\sqrt{p} + \sqrt{q} = 1$.
\item Solve $ (pq - p - q)(z - px - 9y) = pq$.

\markA
\partB

\item The probablity that a bomb dropped from a plane will strike the target
  is 0.2. If 6 bombs are dropped, find the probability that (a) exactly two
  will strike the target. (b) at least two will strike the target. (c) atmost
  two will strike the target.
\item The probability of hitting an aircraft is 0.001 for each shot. How many
  shots should be fired so that the probability with two or more shots is above
  0.95?
\item Solve $u_{k+1} + u_k = 1$ if $u_0 = 0$ using Z-transforms.
\item Prove that $\dfrac{d}{dx}\left(x^{-n} \text{J}_\text{n} (x)\right) = -x^{-n}
  \text{J}_\text{n+1} (x)$.
\item Solve $z^2 (p^2 + q^2 + 1) = a^2$.
\item Solve $(x^2 - y^2 - z^2)p + 2xyp = 2xz$.

\markB

\newpage \again

\partC

\item At an examination 10\% of the students got less than 30 marks and 97\%
  got less than 62 marks. Assuming normal distribution, find $\mu$ and $\sigma$.
  Find the percentage of students who got marks between 40 and 70.
\Or
\item Define the following distributions: (a) Geometric distribution. (b) Hyper
  geometric distribution. (c) Gamma distribution and (d) Uniform distribution.

\item Find the inverse $z$-transform of $\dfrac{z^2 + 3}{(z-1)(z^2+1)}$ by Residue
  method.
\Or
\item Find the inverse $z$-transform of $\dfrac{10z}{z^2 - 3z +2}$ by long
  division method.

\item Prove that $(1 - 2xz + z^2)^{^{-1}\!/_2} = \sum\limits_{n=0}^{\infty}
  \text{P}_\text{n}(x)z^n$.
\Or
\item Prove that $\text{J}_{-\text{n}}(x) = (-1)^n \text{J}_\text{n}(x).$

\item Derive the one dimensional heat equation.
\Or
\item Obtain the D'Alembert's solution of the one dimensional wave equation.

\markC
\ene

\newpage

\mainhead{C 26868}{2}
\semfour{MAY 2012}
\sub {\subj}
\maxtime

\partA

\iitem Define Hyper Geometric distribution.
\item Find the Z-transform of $\cos\left(\dfrac{n\pi}{2}\right)$.
\item Express in terms of Legendre polynomial $ 1 + 2x + x^2$.
\item Solve $ z = px + qy + \sin(p+q)$.
\item Find the binomial distribution with mean 4 and variance $\dfrac{8}{3}$.

\markA
\partB

\item If X is a Poisson variable such the $ p(X=2) = 9p (X=4) + 90p(X=6)$. Find the mean and
  standard deviation.
\item In a hurdle race, a player has to cross 10 hurdles. The probability that he will clear
  each hurdle is $\dfrac{5}{6}$. What is the probability that he will knock down fewer than
  4 hurdles.
\item Find the Z-transform of $f*g$, where $f(n) = u(n),\ g(n) = 2^nu(n)$.
\item Prove that $\text{J}_{{^{-1}}\!/{_2}}(x) = \sqrt{\dfrac{2}{\pi x}}\cos x.$
\item Solve $\left(\dfrac{y-z}{yz}\right)p + \left(\dfrac{z-x}{zx}\right)q = \left(\dfrac{x-y}{xy}\right)$.
\item Solve $u_{n+2} - 4u_{n+1} + 4u_{n} = 0$. given $u_0 = 1$, $ u_1 = 0$.

\markB

\newpage \again

\partC

\item Of a large group of men, 5\% are under 60 inches in height and 40\% are between 60 and 65 inches.
  Assuming a normal distribution, find the mean height and standard deviation. 
\Or
\item If X is uniformly distributed random variable with mean 1 and variance $ \dfrac{4}{3}$, find
\iitem $p(X<0).$
\item $p(|X|<1).$
\item Find $k$ for which $p(X>k)=\dfrac{1}{3}.$
\ene

\item Find the inverse Z-transform of $\dfrac{z}{z^2 - 2z + 2}$ by residue method.
\Or
\item Find the inverse Z-transform of $\dfrac{z^3 - 20z}{(z-2)^3 (z-4)}$ by partial fraction method.

\item Prove that:
\iitem

$\dfrac{d}{dx}\left({x\text{J}_n(x) \text{J}_{n+1}(x)}\right) = \left[\text{J}_n^2(x) -
\text{J}_{n+1}^2 (x) \right]$
\item

$\dfrac{d}{dx}\left({\text{J}_n^2(x) \text{J}_{n+1}^2(x)}\right) = 2\left[\dfrac{n}{2}\text{J}_n^2(x) -
  \dfrac{n+1}{x}\text{J}_{n+1}^2 (x) \right]$
\ene
\Or
\item Show that:
\iitem $\text{P}_{2n}(0) = \dfrac{(-1)^n (2n)!}{2^{2n}(n!)^2}$
\item $\text{P}_{2n+1}(0)=0$
\ene

\item Solve the following partial differential equations:
\iitem $z = p^2 + q^2 $
\item $ q(p-\cos x) = \cos y$
\item $ \sqrt{p} + \sqrt{q} = 1$
\ene
\Or
\item Obtain the D `Alembert's solution of one dimensional wave equation.

\markC
\ene

\newpage

\mainhead{C 15628}{2}
\semfour{JUNE 2011}
\sub {\subj}
\maxtime

\partA

\iitem Define Gamma distribution.
\item Find the Z-transform of $\dfrac{1}{n}$.
\item Show that $\dfrac{2}{5} \text{P}_3(x) + \dfrac{3}{5} \text{P}_1(x) = x^3.$
\item Solve $pq = p+q$.
\item Solve $ z = px + qy + \sqrt{1+ p^2 + q^2}$.

\markA
\partB

\item A machine manufacturing screws in known to produce 3 \% defective. 
  In a random sample of 10 screws, what is the probability that there are (i) Exactly three defectives; (ii)
  Not more than 3 defectives; (iii) No defectives.
\item In a certain factory turning razor blades, there is a small chance of .002 for any blade to be defective.
  The blades are supplied in packets of 10. Use Poisson distribution to calculate the approximate number of packets containing no
  defective, one defective and two defective blades respectively in a 
  consignment of 10,000 packets.
\item Find the inverse Z-transform of $\dfrac{8z^2}{(2z-1)(4z-1)}$.
\item Solve $f(n+2) - 3f(n+1) + 2f(n) = 0;\ f(0) = 0$ and $f(1)=1$, using Z-transforms.
\item Prove that $\dfrac{d}{dx}\left(x{J_n(x) J_{n+1}(x)}\right) = x\left[J_n^2(x) - J_{n+1}^2 (x) \right].$
\item Solve $(z^2 - 2yz - y^2)p + (xy + zx)q = xy - zx.$

\markB

\newpage\again

\partC
\item  In a test on 2000 electric bulbs, it was found that the life of a particular make was normally distributed with an 
  average of 2040 hours and standard deviation of 60 hours. Estimate the number of bulbs likely to burn for:

\begin{enumerate}\item[]
\iitem More than 2150 hours.
\item Less than 1950 hours.
\item More than 1920 hours but less than 2160 hours.
\item Not less than 2,000 hours.
\ene
\ene
\Or
\item \iitem Obtain the Poisson distribution as a limiting case of the Binomial distribution:
\item Define the following distributions:-
\iitem Hyper geometric distribution.
\item Geometric distribution
\item Uniform distribution.
\ene
\ene

\item Find the inverse Z-transform of $\dfrac{z^3 - 20z}{(z-2)(z^2 + 4)}$ by Residue method.
\Or
\item Find the Z-transform of (i) $\dfrac{1}{n(n+1)}$; (ii) $e^{3t}\sin 2t$; (iii) $(t+\text{T})
  e^{-(t+\text{T})}$.
\item Prove that $\text{J}_{-n}(x) = (-1)^n \text{J}_n(x)$.
\Or
\item Prove that $(1 - 2xz + z^2)^{-\frac{1}{2}} = \sum\limits_{n=0}^{\infty}\text{P}_n(x)z^n$.

\item Derive the one dimensional wave equation.
\Or 
\item Obtain the solution of the one dimensional heat equation by the method of separation of variables.

\markC
\ene
