%
% This file is part of Calicut University Question Paper Collection.
%
% Copyright (c) 2012-2015 Mohammed Sadik P. K. <sadiq (at) sadiqpk (d0t) org>.
% License: GNU GPLv3 or later
%
% Calicut University Question Paper Collection is free software: you can
% redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation, either version 3 of the License, or
% (at your option) any later version.
% 
% Calicut University Question Paper Collection is distributed in the hope
% that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
% 
% You should have received a copy of the GNU General Public License
% along with Calicut University Question Paper Collection.
% If not, see <http://www.gnu.org/licenses/>.
% 
%

\def \subj{EN 09 402---ENVIRONMENTAL SCIENCE}

\mainhead{C 26869}{2}
\semfour{MAY 2012}
\sub{\subj}
\maxtime

\partA

\iitem Write the effects of mining on forest.
\item Define food chain and food web.
\item What are consumers in an ecosystem? Classify it with 
  appropriate example.
\item Classify air pollutants with examples.
\item What is meant by sustainable development?

\markA
\partB

\item Explain the benefits and the problems involved in constructing dams.
\item Write short notes on world food problems.
\item What are ecological pyramids?  Explain why some of these pyramids are upright
  while others are inverted in different ecosystems.
\item Define genetic, species and ecosystem diversity with suitable examples.
\item How does landslide take place? Write its effects and explain the steps
  to be taken to prevent this disaster.
\item Write short notes on acid rain and ozone layer depletion.

\markB

\newpage \again

\partC

\item Define renewable energy resources and discuss in detail any {\em one} renewable energy resource.
\Or
\item Discuss in detail the causes and consequences of deforestation.

\item Explain the structure and function of the grassland ecosystem.
\Or 
\item Describe the conservation of biodiversity.

\item Explain the causes, effects and control measures of water pollution.
\Or
\item Discuss in detail the causes and effects of solid waste management.

\item Discuss in detail the principle and advantages of main water harvesting.
\Or 
\item What is meant by ``Energy auditing.'' Explain in detail the problems associated with energy.

\markC
\ene

\newpage

\mainhead{C 15629}{2}

\semfour{JUNE 2011}
\sub{\subj}
\maxtime

\partA

\iitem Write the economic importance of forest.
\item Define ecological pyramid and mention their types.
\item What are the sources of thermal pollution? Mention some of their harmful effects.
\item How does acid rain form? Write its environmental impacts.
\item What is a food chain? Give an example.

\markA
\partB

\item Explain the use and exploitation, environmental effects of extracting mineral sources.
\item Discuss the structure and functions of desert ecosystem.
\item Write a brief notes on noise pollution.
\item Explain in detail the methods of solid waste management.
\item Write a short note on biodiversity and threats to biodiversity.
\item Write a short note on water shed management.

\markB
\partC

\item Discuss in detail the reason and ill-effects of deforestation.
\Or
\item What are renewable and non-renewable energy resources? Discuss any one renewable energy
  resource.

\newpage \again

\item Explain the energy flow in the ecosystem with a suitable example.
\Or
\item Describe In-situ and Ex-situ conservation of biodiversity.

\item Enumerate the causes for water pollution and explain the methods to control it.
\Or
\item What is cyclone? Enumerate its effects and briefly explain the measures to be taken to 
  mitigate this disaster.

\item Discuss the problems related to energy and energy auditing.
\Or
\item List out the reasons for global warming and explain in detail any two of them.

\markC
\ene


