%
% This file is part of Calicut University Question Paper Collection.
%
% Copyright (c) 2012-2015 Mohammed Sadik P. K. <sadiq (at) sadiqpk (d0t) org>.
% License: GNU GPLv3 or later
%
% Calicut University Question Paper Collection is free software: you can
% redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation, either version 3 of the License, or
% (at your option) any later version.
% 
% Calicut University Question Paper Collection is distributed in the hope
% that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
% 
% You should have received a copy of the GNU General Public License
% along with Calicut University Question Paper Collection.
% If not, see <http://www.gnu.org/licenses/>.
% 
%

\def \subj{ AI 09 L05---EMBEDDED SYSTEMS}

\mainhead{41266}{2}
\semsix{MAY 2013}
\sub{\subj}
\maxtime

\partA

\iitem Define an embedded processor.
\item Differentiate between a microprocessor and a microcontroller.
\item What is meant by interrupt service routine?
\item List any two features of PIC16F84 microcontroller.
\item What is a Task?

\markA
\partB

\item How will you distinguish between a hard real-time system and a soft
  real-time system?
\item Name the addressing modes of 8051 microcontroller with example.
\item Draw the diagram for a stepper motor interfacing with 8051 microcontroller.
\item Draw the schematic diagram for a special purpose memory map of
  80196 microcontrollers.
\item Explain the memory organization of 16F84 PIC microcontroller.
\item Explain the contrast between static and dynamic scheduling.

\markB
\partC

\item \iitem Explain about the tools and components required for the designing
  of embedded system.
\Or
\item Explain in detail about real time embedded systems.
\ene

\newpage \again

\item \iitem Explain how keyboard is interfaced with 8051 microcontroller.
\Or
\item Explain about various interrupts of 80196 microcontroller.
\ene

\item \iitem Explain the CPU architecture of 80196 microcontroller.
\Or
\item Explain in detail about the addressing modes of PIC 16F84.
\ene

\item \iitem Discuss in detail about a real time operating system architecture.
\Or
\item Explain task and task states in a real time operating system.
\ene

\markC
\ene

\newpage

\mainhead{26779}{2}
\semsix{MAY 2012}
\sub{\subj}
\maxtime

\partA

\iitem Define embedded system.
\item List any two communication software used in Embedded System.
\item Give reasons why microcontrollers are used in Embedded Systems, and not
  microprocessors.
\item Name the interrupts associated with PIC 16F84.
\item Define pipes and state their function.

\markA
\partB

\item Bring out differences between hard and soft real time systems. Give example.
\item Explain the memory organization of 8051 microcontroller.
\item Draw the schematic showing the interface of temperature sensor to 8051 microcontroller.
\item List the addressing modes of PIC16F84 and give one example for each mode.
\item Differentiate between static and dynamic scheduling methods.
\item What are the issues involved in the selection of an architecture for the design of an Embedded System?

\markB
\partC

\item \iitem Discuss about the various components of Embedded Systems.
\Or
\item Explain about specifications and requirements in an Embedded System.
\ene

\newpage \again

\item \iitem Discuss the various modes of operation of Timer and explain how 8051 can be used
  to generate a square waveform of 1kHz at P1.0 pin in Timer Mode 1.
\Or
\item Explain the steps involved in interfacing a DAC to 8051.
\ene

\item \iitem Explain the memory organization of the PIC microcontroller.
\Or
\item Describe the CPU of 80196 microcontroller.
\ene

\item  \iitem Discuss the Round Robin method of scheduling algorithm.
\Or
\item Explain the salient features of Linux operating system.
\ene

\markC
\ene
