%
% This file is part of Calicut University Question Paper Collection.
%
% Copyright (c) 2012-2015 Mohammed Sadik P. K. <sadiq (at) sadiqpk (d0t) org>.
% License: GNU GPLv3 or later
%
% Calicut University Question Paper Collection is free software: you can
% redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation, either version 3 of the License, or
% (at your option) any later version.
% 
% Calicut University Question Paper Collection is distributed in the hope
% that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
% 
% You should have received a copy of the GNU General Public License
% along with Calicut University Question Paper Collection.
% If not, see <http://www.gnu.org/licenses/>.
% 
%
\def \subj{EN 09 106---BASICS OF CIVIL AND MECHANICAL ENGINEERING}

\mainhead{C 40925}{2}
\comb{APRIL 2013}
\sub{\subj}
\maxtime

\sectionall

\sectionA

\partA

\iitem Give the classification of surveying based on the instruments
  used. \marko{2}
\item What are the constituents of brick? \marko{2}
\item State the uses of cement. \marka

\partBt

\item Define bearing capacity of soil and safe bearing capacity of
  soil. \marko{5}
\item What is roof? Explain the constructional features of RCC roofs.
  \marko{5}
\item Differentiate between place surveying and geodetic surveying.
  \marko{5}

\partCo

\item \iitem State the rules that are followed to calculate the area.
  Explain any one rule in detail.

  \marko{10}
\Or
\item What are the different forms of building stones? Also give the
  characteristics of a good building stone. \marko{10}.
\ene

\item \iitem Explain the differential leveling with a neat sketch.
  \marko{10}
\item What are the different forms of steel sections used in structural
  works? Also state their specific applications.
\ene

\ene

\newpage \again

\sectionB

\partA

\iitem Mention the different types of ignition systems using in SI
  engine. \marko{2}
\item What are the different types of power plants? \marko{2}
\item Define Refrigeration. \marka

\partBt

\item Give the sketch of 4-stroke IC engine to show the various components
  of it and indicate~the~parts.

\marko{5}
\item With a neat sketch, explain the layout of a window room air
  conditioning. \marko{5}
\item Explain the working principle of Gas turbine Power Plant with neat
  sketch. \marko{5}

\partCo

\item \iitem Explain the working principle of four-stroke petrol engine with
  neat sketches. \marko{10}
\Or
\item Draw the layout of a vapour compression refrigeration system, and explain
  the working principle. \marko{10}
\ene

\item \iitem Draw the layout of the steam power plant and explain. \marko{10}
\Or
\item Sketch a diesel power plant and explain its working principle. Also state
  its merits and demerits. \marko{10}
\ene

\ene

\newpage

\mainhead{C 26476}{2}
\comb{APRIL 2012}
\sub{\subj}
\maxtime

\sectionall

\sectionA

\partA

\iitem Name the types of stone masonry. \marko{2}
\item What are the advantages of reinforced cement concrete?  \marko{2}
\item Define transportation.  \marka

\partBt

\item 
  Name the different types of stone masonry. Explain them in detail with a neat sketch.

 \marko{5}
\item Define workability of concrete. Explain briefly about slump test.  \marko{5}
\item Write short notes on Raft or Mat foundation. \marko{5}

\partCo

\item \iitem Explain in detail about single Flemish and double Flemish bond.  \marko{10}
\Or
\item Briefly describe the Engineering properties and applications for the following:
\iitem Cement. \item Brick. \item Timber.  \marko{10}
\ene\ene

\item \iitem 
  Explain about the types and functions of the following structural components of buildings:
\iitem Foundation. \item Arch and lintels.  \marko{10}
\ene
\Or
\item Define a bridge and Explain the components of a bridge with a neat sketch.   \marko{10}
\ene
\ene

\newpage \again

\sectionB

\partA

\iitem Give the classification of SI engines.  \marko{2}
\item State second law of thermodynamics.  \marko{2}
\item Is it necessary to prime all the types of pumps?   \marka

\partBt

\item Derive the air-standard efficiency of diesel cycle.   \marko{5}
\item Compare between the different forging operations.  \marko{5}
\item Draw the layout of Gas turbine power plants.  \marko{5}

\partCo

\item \iitem How does a hydroelectric power plant work? Explain with the help of schematic diagrams.

  \marko{10}
\Or
\item Explain the following with the help of necessary figures:
\iitem Die casting.
\item Oxy-acetylene welding.  \marko{10}
\ene\ene


\item \iitem A Carnot refrigeration cycle absorbs heat at 256 K and rejects at 303 K. Calculate the COP of
the refrigeration cycle. If the Carnot heat pump operates between the same temperature limits as the
  above cycle, what is COP? How many kJ/s
  will the heat pump delivers at 303 K if it absorb 1200 kJ/min.   \marko{10}
\Or
\item Explain in detail about the closed cycle and open cycle gas turbine. \marko{10}
\ene
\ene

\newpage

\mainhead{C 15009}{2}
\comb{MAY 2011}
\sub{\subj}
\maxtime

\sectionall

\sectionA

\partA

\iitem What are the functions of a Civil Engineer? \marko{2}
\item Name the different types of beams. \marko{2}

\item Surveying is defined as the process of measuring ------------ distances, ------------ distances and
  ------------ angles in order to determine the location of points on, above or below the earth surface.

 \marka

\partBt

\item Compare between English and Flemish bond.  \marko{5}
\item Explain about the temporary adjustments of a leveling instrument. \marko{5}
\item What are the factors influencing the selection of a bridge? \marko{5}

\partCo

\item \iitem Compare between Brick masonry and Stone masonry.
\Or 
\item Write in detail about the properties of concrete.
\ene

\item \iitem Draw a neat sketch by showing the cross-sectional detail of a gravity dam and explain its
  features.
\Or 
\item \iitem Define super elevation. Explain the purpose of super elevation.  \marko{6}
\item Find the super elevation to be provided to the carriageway of a road on a horizontal curve
  of radius 200 m. The average speed of vehicles may be taken as 45 Km/hr.

\marko{4}
\ene
\ene
\ene

\newpage \again

\sectionB

\partA

\iitem Distinguish between Carburettor type and MPFI engines.  \marko{2}
\item What is meant by priming of pumps? Is it necessary to prime all the types of pumps?  \marko{2}
\item Give the classifications of IC engines. \marka

\partBt

\item Draw the layout of Nuclear power plants.  \marko{5}
\item Compare between two stroke and four stroke engines. \marko{5}
\item Show the relationship between Power transmitted by a belt system; belt tension and
  coefficient of friction.  \marko{5}

\partCo

\item \iitem Explain the following with the help of necessary figures:-
\iitem CRDI engines.
\item Otto cycles.
\item Tidal power plants.
\ene
\Or
\item Explain in detail of the first law of thermodynamics with internal energy concept.
\ene

\item \iitem Write a detailed note on centrifugal pumps.
\Or
\item Write short notes on:
\iitem Sand casting processes.
\item Hydrostatic extrusion.
\item 3 roll process.
\ene
\ene
\ene

\markany{2}{10}{20}

\newpage

\mainhead{C 6289}{2}
\comb{MAY 2010}
\sub{\subj}
\maxtime

\sectionall

\sectionA

\partA

\iitem Explain about Laterite stone. \marko{2}
\item Define header and strecher. \marko{2}
\item Define magnetic bearing. \marka

\partBt

\item Explain in detail about the test and characteristics of good bricks. \marko{5}
\item What are the various types of cement? Write about the properties and uses of cement. \marko{5}
\item Write the types and functions of the column. \marko{5}
\partCo
\item \iitem Define Surveying. Briefly describe about chain and accessories.
\Or
\item Draw a neat sketch of a bowstring girder bridge. Explain in detail.

 \marko{10}
\ene

\item \iitem Draw a neat sketch of English bond (1 brick wall and 1$\frac{1}{2}$ brick wall
  thickness). Explain in brief.
\Or
\item What are the properties and applications of cement mortar and cement concrete.
\ene

 \marko{10}
\ene

\newpage \again

\sectionB
\partA

\iitem Draw an ideal PV diagram of a our stroke SI engine (Otto cycle). \marko{2}
\item Write short notes on diesel power plants. \marko{2}
\item Name the main elements in the transmission system. \marka

\partBt

\item Derive the efficiency of the Brayton cycle. \marko{5}
\item Write short notes on carburettor and MPFI engines. \marko{5}
\item Write a short note on 2 roll process. \marko{5}

\partCo

\item \iitem A pump develops a head of 10 m. of water column. The discharge is 600 litres/min.
  Determine the motor power if the overall efficiency is 0.5 and the medium pumped is water.
\Or
\item Discuss in detail about the slider crank mechanism.

 \marko{10}
\ene

\item \iitem \iitem Compare four stroke and two stroke engine. \marko{5}
\item Compare between SI and CI engine. \marko{5}
\ene
\Or
\item Explain in detail about the refrigeration and air conditioning with a neat sketch.

 \marko{10}
\ene \ene
