%
% This file is part of Calicut University Question Paper Collection.
%
% Copyright (c) 2012-2015 Mohammed Sadik P. K. <sadiq (at) sadiqpk (d0t) org>.
% License: GNU GPLv3 or later
%
% Calicut University Question Paper Collection is free software: you can
% redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation, either version 3 of the License, or
% (at your option) any later version.
% 
% Calicut University Question Paper Collection is distributed in the hope
% that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
% 
% You should have received a copy of the GNU General Public License
% along with Calicut University Question Paper Collection.
% If not, see <http://www.gnu.org/licenses/>.
% 
%

\def \subj{EN 09/PTEN 09 103---ENGINEERING PHYSICS}

\mainhead{C 40921}{2}
\comb{APRIL 2013}
\sub{\subj}
\maxtime

\partA

\iitem What is the difference between optical and geometrical paths?
\item Explain reciprocal lattice.
\item What is the physical meaning of numerical aperture?
\item Explain Avalanche breakdown.
\item What is stationary state?

\markA
\partB

\item Explain the formation of Newton's ring and show that the radius
  of the $n^\text{th}$ dark ring is proportional to the under roof
  of wavelength.
\item Prove the reciprocal lattice of BCC is FCC.
\item The volume of hall is 475 cm$^3$. Suppose the wall has an area of
  200 m$^3$, and it contains two open windows, each having an area of
  25 m$^3$. The area of floor and ceiling of the hall is 100 m$^3$ each.
  If the absorption coefficient of the wall, ceiling and floor are 0.025,
  0.02 and 0.55 respectively, calculate the reverberation time of the hall.
\item Electrons are accelerated through 300 V and are reflected from a
  crystal. If the first order reflection maximum occurs at a glancing angle
  of 60 degrees, calculate the inter-planar distance.
\item Derive the expression for numerical aperture of step index fiber.
  Show that it does not depend on the physical dimension of the fiber.
\item Explain how the Fermi level changes with the increasing amount of
  impurity in $n$-type and $p$-type semiconductor.

\markB

\newpage \again

\partCo

\item \iitem Explain why thin film observed in sunlight exhibit colours. Why
  does an excursing thin film of uniform thickness seen by reflected light
  shows no colour but appears dark? Deduce the condition.
\Or
\item Explain the Bravais lattice of three dimensional crystal systems.
\ene

\item \iitem Explain the principle and working of He-Ne laser with energy level
  diagram.
\Or
\item Explain the basic structure of optical fiber with suitable diagrams.
  Distinguish between step index fiber and graded index fiber.
\ene

\item \iitem What is Meissner effect? Explain the properties of Type I and Type \
  II super conductors with suitable diagrams and examples.
\Or
\item Explain the characteristics of an NPN transistor in CE configuration.
\ene

\item \iitem Derive the eigen functions and eigen values of particle in
  a box problem.
\Or
\item Explain the principle and working of acoustic grating with diagram.
\ene

\markC
\ene

\newpage

\mainhead{C 26472}{2}
\comb{APRIL 2012}
\sub{\subj}
\maxtime

\partA

\iitem Explain the conditions for interference.
\item What do you understand by extrinsic and intrinsic semiconductors?
\item Explain the principle of piezoelectric effect.
\item Write a note on Miller indices.
\item Why nanomaterials are superior when compared to bulk materials?

\markA
\partB

\item How do you find specific rotation of sugar solution using half shade polarimeter? Deduce
  the concentration of the sugar solution. 
\item A He-Ne laser of wavelength 6328 \AA{} is emitting beam with an average power of 1mW is
  focused on a circle
  of radius 2 mm. Find the intensity of the focused beam. Compare this with intensity of
  60W bulb on a person standing 3 m away.
\item The numerical aperture of an optical fiber is 0.2, when surrounded by air. If the
  refractive index of cladding
  is 1.59, find the acceptance angle of the fiber in water with refractive index 1.33.
\item The expression for Fermi energy in case of intrinsic semiconductor is $\text{E}_{\text{f}} =
  \text{E}_{\text{g}}/2$. But
  this expression is obtained by making some assumption. What are these assumptions?
\item Explain how the reverberation time affects the acoustic of a building. Also give a brief
  account of corrective measures.
\item Discuss the de Broglie's concept of matter waves. What are all the physical significances
  of wave function $\Psi$?

\markB

\newpage \again

\partCo
\item 
\iitem Write a simple theory of diffraction using grating and determine the wavelength of
  monochromatic light.
\Or
\item Obtain packing fraction calculation on SC, BCC and FCC.
\ene

\item \iitem Show that under thermal equilibrium, laser action is not possible in visible region
  at room temperature. At what temperature the laser action is possible and is it realizable?
\Or
\item Explain the basic principle of holography. Explain recording and reconstruction of holograms. 
    Write application of holography.
\ene

\item
\iitem Explain voltage and current characteristics of PN junction diode when it is reverse biased.
  Explain amplifier characteristics of NPN transistor.
\Or
\item How does the Fermi level change with temperature in extrinsic semiconductor? Discuss the effect of
    increasing amount of dopants in extrinsic semiconductor.
\ene

\item 
\iitem Explain the basic postulates of the quantum mechanics. Derive the Schr$\ddot{\text{o}}$dinger
  equation for the free particle.
\Or
\item What is piezoelectric crystal? How can it be used for the production of longitudinal ultrasonic
    waves through oscillator circuit?
\ene

\markC
\ene

\newpage

\mainhead{C 15005}{2}
\comb{MAY 2011}
\sub{\subj}
\maxtime

\partA

\iitem Explain the phenomenon of double refraction in calcite crystal.
\item Write the Bragg diffraction equation in reciprocal lattice.
\item Why population inversion is necessary to achieve lasing action?
\item What is static and dynamic resistance of Zener diode?
\item Explain the physical meaning of wave function.

\markA
\partB

\item What is half-wave plate? Explain its action in polarized light incident on it with its electric
  vector E making an angle $\theta$ with the optic axis of the half-wave plate.
\item
\iitem Derive the expression for the distance between the atomic planes such as (100) and (110) planes.
\item X-rays of wavelength 0.71 \AA{} are reflected from (110) plane of a rock salt crystal
  ($a=$~2.82~\AA{}). Calculate the glancing angle corresponding to second order reflection.
\ene

\item If a 15g marble is moving with speed of 1/3 m/s and is confined over a distance of 12 cm, find the
  total number of energy levels. What do you infer from the results?
\item What is magnetostriction effect? Draw circuit diagram of magnetostriction oscillator, explain its
  working.
\item Explain how the Fermi level changes with the increasing amount of impurity in $n-$type and $p-$type
  semiconductor.
\item Explain the different types of fibers and list out the applications of fibers.

\markB

\newpage \again

\partC
\item
\iitem Explain why thin film observed in sunlight exhibit colours. When does an excursing thin film
  of uniform thickness seen by reflected light shown no colour but appears dark?
\Or
\item How does the Fermi level change with temperature in extrinsic semiconductor? Discuss the 
  effect of increasing amount of dopants in extrinsic semiconductor.
\ene

\item
\iitem Explain simulated emission process. Describe the construction and working of Nd:YAG laser with 
  band diagram.
\Or
\item Derive Sabine's formula for reverberation time.
\ene

\item 
\iitem Explain the properties of Type I and Type II superconductors with suitable
  diagrams. List out applications of superconductors.
\Or
\item Explain liquid crystal used as a display device. Explain with suitable circuit diagram.
\ene

\item 
\iitem Solve the Schr$\ddot{\text{o}}$dinger equation for a particle confined in a
  one-dimensional box of length L. Draw the first few energy levels and the corresponding
  eigenfunctions.
\Or
\item Explain amplifier characteristics of NPN transistor.
\ene

\markC
\ene

\newpage


\mainhead{C 6285}{2}
\comb{MAY 2010}
\sub{\subj}
\maxtime

\partA

\iitem How can Newton rings experiment be used to determine refractive index of liquid?
\item What is the difference between unit cell and primitive cell?
\item Why population inversion is necessary to achieve in lasing action?
\item Explain zener breakdown.
\item  What are called nanomaterials?

\markA
\partB

\item What is half wave plate? Explain its action on polarized light incident on it with its
  electric vector E making an angle $\theta$ with the optic axis of the half wave plate.
\item Derive the expression for the distance between the atomic planes such as (100) and (110) planes
  of the cubic crystals.
\item The position and momentum of a 1 keV electron are simultaneously determined. If its position is
  located within 0.1 nm, what is the percentage of minimum uncertainty in its momentum?
\item Consider a range of light entering 2 m. long step index fiber, whose refractive index arid diameter
  of the core are 1.48 and 60 $\mu$m respectively. If the incident ray makes an angle of 3.43$^{\circ}$ with the
  axis of the fiber, how many reflections will it undergo within the fiber?
\item Explain how the Fermi level changes with the increasing amount of impurity in $n$-type and $p$-type
 semiconductor.
\item Explain the properties and applications of carbon nanotubes (CNT).

\markB

\newpage \again

\partCo

\item \iitem Explain the following:-
\iitem Double refraction.
\item Optic axis
\item Positive
  and negative refractive index crystals.
\ene

  How can we experimentally distinguish between plane polarized, circularly polarized and 
  elliptically polarized light.
\Or
\item Explain:
\iitem Basic principle of holography.
\item Recording and reconstruction of holograms.
\ene
\ene

\item \iitem Explain population inversion. Describe the construction and working of a semiconductor
  laser with band diagram.
\Or
\item Explain how the reverberation time affects the acoustic of a building. Also give a brief account
  of corrective measures.
\ene

\item \iitem Explain the phenomenon involved at junction of the superconductor using A.C. Josephson effect.
\Or
\item Explain the principle and working of LED with suitable diagram.
\ene

\item \iitem Derive Schr$\ddot{\text{o}}$dinger time dependent and time independent equation.
\Or
\item What is piezoelectric crystal? How can it be used for the production of longitudinal ultrasonic
  waves through oscillator circuit?
\ene

\markC
\ene
