%
% This file is part of Calicut University Question Paper Collection.
%
% Copyright (c) 2012-2015 Mohammed Sadik P. K. <sadiq (at) sadiqpk (d0t) org>.
% License: GNU GPLv3 or later
%
% Calicut University Question Paper Collection is free software: you can
% redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation, either version 3 of the License, or
% (at your option) any later version.
% 
% Calicut University Question Paper Collection is distributed in the hope
% that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
% 
% You should have received a copy of the GNU General Public License
% along with Calicut University Question Paper Collection.
% If not, see <http://www.gnu.org/licenses/>.
% 
%

\def \subj{ AI 09 603---BIO MEDICAL INSTRUMENTATION}

\mainhead{C 41261}{2}
\semsix{MAY 2013}
\sub{\subj}
\maxtime

\partA

\iitem What do you mean by biometrics?
\item Name the different types of electrodes used for ECG measurement.
\item Define mean Arterial pressure.
\item What is a bronchospirometer?
\item What are the applications of telemedicine?

\markA
\partB

\item Briefly explain respiratory system.
\item Explain the electro-conduction system of heart?
\item With schematic explain oscillometric method of blood pressure measurement.
\item Write a note on artificial heart valves.
\item Describe the physiological effect of electric current on human body.
\item List the applications of X-rays in medical field.

\markB
\partCo

\item \iitem Explain the terms:
\iitem resting potential.
\item action potential.
\ene
\Or

\newpage\again

\item With schematic explain any \emph{two} transducers used for biomedical application.
\ene

\item \iitem Describe the measurement technique used for measuring cardiac output.
\Or
\item With block schematic explain the working of ECG machine.
\ene

\item \iitem With schematic describe the working of a heart lung machine.
\Or
\item Describe the principle of operation of spirometer.
\ene

\item \iitem With block schematic, explain the working of surgical diathermy machine.
\Or
\item With schematic describe the operation of ultrasonic imaging system.
\ene

\markC
\ene

\newpage

\mainhead{C 26774}{2}
\semsix{MAY 2012}
\sub{\subj}
\maxtime

\partA

\iitem Name the major physiological systems of the body.
\item What is meant by refractory period?
\item Distinguish between systolic and diastolic BP.
\item What do you mean by fibrillation?
\item What is the principle of diathermy?

\markA
\partB

\item List and explain the components of a man instrument system.
\item What is meant by resting membrane potential?
\item Draw and explain a typical ECG waveform.
\item With schematic explain the structure of a neuron.
\item With block diagram explain the working of EMG machine.
\item List any four properties of X-rays.

\markB

\newpage \again

\partCo

\item \iitem With schematic explain
\iitem Surface electrode \item Needle electrode
\ene
\Or
\item Explain any two types of transducers used in bio-medical field.
\ene

\item \iitem Explain the indirect method of blood pressure measurement.
\Or
\item With block schematic explain the working of ultrasonic blood flow meter.
\ene

\item \iitem Explain the working of cardiac pacemaker with the help of block diagram.
\Or
\item With schematic describe the operation of Heart-Lung machine.
\ene

\item \iitem With block diagram explain the working of Magnetic Resonance Imaging system.
\Or
\item With schematic explain the principle of angiography.
\ene

\markC
\ene

