%
% This file is part of Calicut University Question Paper Collection.
%
% Copyright (c) 2012-2015 Mohammed Sadik P. K. <sadiq (at) sadiqpk (d0t) org>.
% License: GNU GPLv3 or later
%
% Calicut University Question Paper Collection is free software: you can
% redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation, either version 3 of the License, or
% (at your option) any later version.
% 
% Calicut University Question Paper Collection is distributed in the hope
% that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
% 
% You should have received a copy of the GNU General Public License
% along with Calicut University Question Paper Collection.
% If not, see <http://www.gnu.org/licenses/>.
% 
%
\def \subj{ AI 09 L17---POWER PLANT INSTRUMENTATION AND CONTROL}




\mainhead{C 44473}{2}

\semseven{JUNE 2013}

\sub{\subj}

\maxtime


\partA


\iitem  What are condensers?

\item Distinguish between two element drum level control and three element drum level control.

\item Define pH.

\item List out advantages of distributed control in power plants.

\item What is nuclear fission?

\markA
\partB

\item How will you generate power from wind?

\item Explain the method of measuring flow of feed water in power plant.

\item Mention the functions of combustion control.

\item Why should the pressure of steam be raised in boiler and turbine?

\item How will you automate a thermal power plain using SCADA?

\markB
\partC

\item \iitem Explain in detail about various types of boilers.

\Or

\item Explain the operation of a thermal power plant with a neat block diagram.

\ene

\item \iitem Explain dust monitors with a neat sketch.

\newpage \again

\Or

\item Explain the working principle of pH meter.

\ene


\item \iitem Explain in detail about parallel position control system for combustion control.

\Or

\item With a neat block diagram, explain the functions of a distributed control system for 
  power plant.      

\ene

\item \iitem Explain briefly about cooling system in a power plant.

\Or


\item Explain in detail about hydroelectric power generation with a neat sketch.

\ene

\markC

\ene


\newpage


\mainhead{C 29767}{2}

\semseven{OCTOBER 2012}

\sub{\subj}

\maxtime


\partA


\iitem What are the basic building blocks of a thermal power plant?

\item What are the precautions required in a nuclear power plant?

\item Define power factor.

\item List out the advantages of superheaters.

\item What is SCADA?

\markA
\partB


\item State the importance of instrumentation in power generation.

\item Explain in detail about turbine generators.

\item Write short notes on pollution monitoring instruments.

\item Explain in detail about two element drum level control.

\item What are interlocks?

\item Discuss the measurement of monitoring speed in a turbine.



\markB

\partC

\item \iitem Explain in detail about various types of boilers.

\Or

\item Explain in detail about non-conventional methods of power generation.

\ene

\newpage \again

\item \iitem Explain the working principle of a dissolved oxygen analyzer.

\Or

\item Explain in detail about the  measurement of frequency in a power plant.

\ene


\item \iitem Write short notes on combustion control.

\Or

\item Explain the role of distributed control system in power plants.

\ene

\item \iitem Explain the PLC based automation strategy of a thermal power plant.

\Or

\item Explain in detail about Hydro-electric power generation.

\ene

\markC

\ene




