%
% This file is part of Calicut University Question Paper Collection.
%
% Copyright (c) 2012-2015 Mohammed Sadik P. K. <sadiq (at) sadiqpk (d0t) org>.
% License: GNU GPLv3 or later
%
% Calicut University Question Paper Collection is free software: you can
% redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation, either version 3 of the License, or
% (at your option) any later version.
% 
% Calicut University Question Paper Collection is distributed in the hope
% that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
% 
% You should have received a copy of the GNU General Public License
% along with Calicut University Question Paper Collection.
% If not, see <http://www.gnu.org/licenses/>.
% 
%
\def \subj{ AI 09 L11---COMPUTER NETWORKS}



\mainhead{D 50568}{2}

\semseven{NOVEMBER 2013}

\sub{\subj}

\maxtime

\partA


\iitem Draw the internet protocol stack and structure of internet.

\item What are the services supported by transport layer?

\item State two additional features of ABR services over UBR services.

\item What is a switch?

\item What is a bridge?

\markA
\partB

\item Explain briefly about FTP.

\item Explain briefly about DNS.

\item Explain the principles of congestion control in a network.

\item Explain IPV6 packet format.

\item Write notes on Hash functions.

\item Explain briefly any one multiple access protocol.

\markB

\partC

\item Explain the various switching techniques used in networks.

\Or

\item Explain about internet's directory service.

\newpage \again

\item Explain two techniques used to ensure reliable data transfer in a
  network.

\Or

\item Explain the congestion control used in TCP networks.

\item Explain briefly about multicast routing.

\Or

\item Explain IGMP for IPV6

\item Explain on:
  \iitem Authentication protocols
  \item Firewalls.
  \ene

\Or

\item Explain  an error detecting and correcting technique.

\markC

\ene

\newpage

\mainhead{C 29765}{2}

\semseven{OCTOBER 2012}

\sub{\subj}

\maxtime


\partA


\iitem What are the two types of services that Internet provides  to its applications? Write two characteristics of each of these services.

\item What is the difference between persistent HTTP with pipelining and persistent HTTP without pipelining.

\item What is UDP?

\item What is a datagram?

\item State the services of data link layer of a network.


\markA

\partB


\item Explain about loss incurred in packet-switched networks.

\item Write notes on electronic mail.

\item Explain briefly on multiplexing and demultiplexing network applications.

\item Explain intra-As and inter-As routing protocols.

\item Explain multicast routing using a source-based tree.

\item Explain on point-to-point protocol.


\markB

\partCo

\item \iitem Explain about various physical media used in networks.

\Or


\item Explain on FTP.


\newpage
\again


\ene

\item \iitem Explain a selective repeat protocol.

\Or

\item Explain about TCP.

\ene

\item \iitem Explain on hierarchical routing.

\Or

\item Explain on IPv6.

\ene

\item \iitem Explain Carrier-sense multiple access protocol.

\Or

\item Explain briefly on ATM network.

\ene

\ene

