%
% This file is part of Calicut University Question Paper Collection.
%
% Copyright (c) 2012-2015 Mohammed Sadik P. K. <sadiq (at) sadiqpk (d0t) org>.
% License: GNU GPLv3 or later
%
% Calicut University Question Paper Collection is free software: you can
% redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation, either version 3 of the License, or
% (at your option) any later version.
% 
% Calicut University Question Paper Collection is distributed in the hope
% that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
% 
% You should have received a copy of the GNU General Public License
% along with Calicut University Question Paper Collection.
% If not, see <http://www.gnu.org/licenses/>.
% 
%



\def \subj{ EC/PTEC/AI/EE/ATEE/BM/IC 09 602---\\
  ENGINEERING ECONOMICS AND PRINCIPLES OF MANAGEMENT}

\mainhead{C 61438}{2}
\semsix{MAY 2014}
\sub{\subj}
\maxtime

\separate
\sectionEE
\partA

\iitem Define opportunity cost. \marko{2}
\item Compare primary functions, secondary functions and tertiary functions. \marko{2}
\item What are the ways to improve productivity? \marka

\partBt

\item Mention the functions of commercial banking.  \marko{5}
\item Write short notes on foreign trade policy.  \marko{5}
\item What is process planning?  \marko{5}

\partC

\item Explain in detail about the concepts of inflation and deflation. \marko{10}
\Or
\item Discuss in detail about the law of supply and demand. \marko{10}

\item Explain in detail about ARR and NPV methods of project analysis. \marko{10}
\Or
\item Explain in detail about single payment present worth factor and equal payment series
  capital recovery factor. \marko{10}

\ene

\newpage \again

\sectionPM

\partA

\iitem What is merit rating? \marko{2}
\item Name the phases of project management. \marko{2}
\item What are the components of cost? \marka

\partBt

\item Compare tactical and operational decisions. \marko{5}
\item What are the basic concepts of ledger? \marko{5}
\item What is the need for decision trees? \marko{5}

\partC

\item Explain in detail about the theory and functions of management
  organizational structure.

\marko{10}
\Or
\item Discuss in detail about recruitment process and training. \marko{10}

\item Explain in detail about basic concepts related to marketing environment. \marko{10}
\Or
\item Explain in detail about Critical Path Method for project management. \marko{10}

\ene

\newpage

\mainhead{41235}{2}
\semsix{MAY 2013}
\sub{\subj}
\maxtime

\separate
\sectionEE
\partA

\iitem Define Marginal Cost. \marko{2}
\item What is an ARR? \marko{2}
\item What is IRR? \marka

\partBt

\item Explain economic reasoning and economic efficiency. \marko{5}
\item Explain the functions of money. \marko{5}
\item Explain process planning. \marko{5}

\partCo

\item Explain Law of supply and demand. \marko{10}
\Or
\item Discuss the functions and role of Commercial banking. \marko{10}

\item Explain single payment
\iitem Compound amount factor and
\item present worth factor. \marko{10}
\ene
\Or
\item Explain the methods of project analysis and break even analysis. \marko{10}

\ene

\newpage \again

\sectionPM

\partA

\iitem What is an organization? \marko{2}
\item What is CPM? \marka
\item Give any two functions of Management. \marko{2}

\partBt

\item Explain the evolution of management theory. \marko{5}
\item With a suitable example, explain the decision tree.  \marko{5}
\item What is the significance of a Balance sheet? Explain. \marko{5}

\partCo

\item Explain the functions and principles of management.  \marko{10}
\Or
\item Discuss in detail about Job analysis.  \marko{10}

\item Explain the elements and components of Cost. \marko{10}
\Or
\item Discuss in detail about Marketing Management. \marko{10}

\ene

\newpage

\mainhead{C 26748}{2}
\semsix{MAY 2012}
\sub{\subj}
\maxtime

\separate
\sectionEE
\partA

\iitem Define Economic efficiency. \marko{2}
\item What is the aim of value analysis? \marka
\item What is process planning? \marko{2}

\partBt

\item Explain inflation and Deflation. \marko{5}
\item Explain the time value of Money. \marko{5}
\item Explain the functions of commercial banking. \marko{5}

\partCo

\item Discuss the Law of Supply and Demand. \marko{10}
\Or
\item Discuss the Economic Policy Reforms in India. \marko{10}

\item Explain in detail about:
\iitem single payment compound amount factor.
\item Equal payment series capital recovery factor. \marko{10}
\ene
\Or
\item Discuss the various methods of Project analysis. \marko{10}

\ene

\newpage \again

\sectionPM

\partA

\iitem Define Management. \marko{2}
\item Define Profit and Loss.  \marko{2}
\item What is the significance of PERT?  \marka

\partBt

\item Explain the decision making process.  \marko{5}
\item Briefly explain financial management.  \marko{5}
\item With a simple example, explain Balance Sheet.  \marko{5}

\partCo

\item Describe the principles and types of an Organizational structure.  \marko{10}
\Or
\item Discuss in detail about Human Resource Management.  \marko{10}

\item Discuss in detail about the basics of accounting. \marko{10}
\Or
\item Discuss in detail about the basic concepts of Marketing management.  \marko{10}

\ene
