%
% This file is part of Calicut University Question Paper Collection.
%
% Copyright (c) 2012-2015 Mohammed Sadik P. K. <sadiq (at) sadiqpk (d0t) org>.
% License: GNU GPLv3 or later
%
% Calicut University Question Paper Collection is free software: you can
% redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation, either version 3 of the License, or
% (at your option) any later version.
% 
% Calicut University Question Paper Collection is distributed in the hope
% that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
% 
% You should have received a copy of the GNU General Public License
% along with Calicut University Question Paper Collection.
% If not, see <http://www.gnu.org/licenses/>.
% 
%

\def \subj{AI 09 504---COMPUTER ORGANISATION AND ARCHITECTURE}

\mainhead{50629}{2}
\semfive{NOVEMBER 2013}
\sub{\subj}
\maxtime

\partA

\iitem What is a machine cycle?
\item What are the two types of microinstructions and their attributes?
\item Distinguish between floating point and fixed point representations.
\item What does I/O interrupt make more efficient use of the CPU?
\item What is vector processing.

\markA
\partB

\item Evaluate x = (A + B) $\times$ (C + D) using various types of
  instructions.
\item What are the most common fields found in an instruction? Explain.
\item Write a note on Virtual Memories.
\item With a suitable example, explain signed addition and subtraction.
\item Explain Magnetic-Disk and CD-ROM systems.
\item Explain interleaved memory organizations.

\markB
\partC

\item \iitem With block diagram explain the functional units and their
  operations of Computer Hardware.
\Or

\newpage \again

\item With suitable examples explain the various addressing modes.
\ene

\item \iitem Design a Hardwired control and PLA control for a Binary
  Multiplier.
\Or
\item Explain in detail about Fully Associative Mapping and Set Associative
  Mapping.
\ene

\item \iitem Discuss in detail about pipelining and its influence on set
  design.
\Or
\item Explain: \iitem Communication with remote terminals and
\item Communication Line considerations.\ene
\ene

\item \iitem Explain in detail about the principle of pipelining and its
  architectural classification.
\Or
\item Discuss in detail about SIMD array processor.
\ene

\markC
\ene

\newpage

\mainhead{30971}{2}
\semfive{NOVEMBER 2012}
\sub{\subj}
\maxtime

\partA

\iitem What is machine cycle?
\item What is a microprogram?
\item What is a cache memory?
\item Name any four storage devices.
\item What are interleaved memory?

\markA
\partB

\item What are subroutines? Give an example.
\item What are read only memories? Explain.
\item With a suitable example, explain signed
  addition and subtraction.
\item Write a note on graphic input devices.
\item Explain SIMD array processor.
\item Briefly explain the floating point number representation.

\markB
\partC

\item \iitem With block diagram, explain the basic structure of a 
  computer.
\Or
\item Explain the various addressing modes in detail.
\ene

\newpage \again

\item \iitem \iitem Explain DMA
\item Explain the performance considerations in memories.
\ene
\Or
\item With a suitable example explain the algorithm for multiplication
  of signed numbers.
\ene

\item \iitem Discuss in detail about pipelining and its types.
\Or

\item Discuss in detail about pipelining and its types.
\Or
\item Explain in detail about
\iitem system performance considerations
\ene
\ene


\item \iitem Discuss in detail about parallel processing.
\Or
\item \iitem Explain the interleaved memory organizations.
\item What are the requirements of vector processing? Explain.
\ene
\ene
 
\markC
\ene

\newpage

\mainhead{20920}{2}
\semfive{OCTOBER 2011}
\sub{\subj}
\maxtime

\partA

\iitem What is a stack?
\item What is a virtual memory?
\item Perform the following subtraction using signed binary number
  representation: ($24_{10} - 16_{10}$)
\item What is an instruction queue?
\item What is a SIMD stream?

\markA
\markB

\item What is a machine cycle? Explain.
\item What is register gating? Explain.
\item With block diagram explain the input output organization of
  a Computer.
\item With an example, explain the branching condition.
\item Write a note on Flat Panel displays.
\item Briefly explain any one application of parallel processing.

\markB
\ene
