%
% This file is part of Calicut University Question Paper Collection.
%
% Copyright (c) 2012-2015 Mohammed Sadik P. K. <sadiq (at) sadiqpk (d0t) org>.
% License: GNU GPLv3 or later
%
% Calicut University Question Paper Collection is free software: you can
% redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation, either version 3 of the License, or
% (at your option) any later version.
% 
% Calicut University Question Paper Collection is distributed in the hope
% that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
% 
% You should have received a copy of the GNU General Public License
% along with Calicut University Question Paper Collection.
% If not, see <http://www.gnu.org/licenses/>.
% 
%

\def \subj{AI 09 505---POWER ELECTRONICS}

\mainhead{D 70301}{2}
\semfive{NOVEMBER 2014}
\sub{\subj}
\maxtime

\partA

\iitem What is power transistor?
\item What is MCT?
\item Define power factor.
\item What is a chopper
\item What is an isolation amplifier?

\markA
\partB

\item Explain an application each for GTO and power MOSFET.
\item What are power diodes? Briefly explain its types.
\item Explain a method for power factor improvement.
\item Explain the classification of choppers.
\item Write notes on switched mode power supply.
\item Briefly explain on synchronization circuits.

\markB
\partC

\item Explain the working of TRIAC with its characteristics and explain
  one application of it.
\Or
\item Explain the working of SCR with its characteristics and explain one
  application of it.

\newpage \again

\item Explain the working of three-phase converter circuit.
\Or
\item Explain the working of cyclo converter.

\item Explain about MOSFET/IGBT choppers.
\Or
\item Explain the working of McMurray Bedford inverter.

\item Explain the working of buch boost regulators.
\Or
\item Explain simple drive circuits using power BJT, MOSFET and IGBT.

\markC
\ene

\newpage

\mainhead{D 50630}{2}
\semfive{NOVEMBER 2013}
\sub{\subj}
\maxtime

\partA

\iitem State the types of power diodes.
\item What is a power transistor?
\item What is a controlled rectifier?
\item State two applications of D.C. choppers.
\item Define Load regulation.

\markA
\partB

\item Write briefly on MCT.
\item Write notes on GTO.
\item Explain briefly the working of single phase converter.
\item Explain the working principle of a D.C. chopper.
\item Draw the block diagram of UPS and explain its types.
\item Draw a simple drive circuit using power MOSFET and explain.

\markB
\partC

\item Explain the working of TRIAC with its characteristics.
\Or
\item Explain the working of IGBT with its characteristics.

\newpage \again

\item \iitem  Explain a method for power factor improvement.
\item Write notes on cyclo converters.
\ene
\Or
\item Explain the method of A.C. voltage controller circuits.

\item \iitem Explain the working of MOSFET/IGBT chopper.
\item Explain the vector control of induction motors.
\ene
\Or
\item Explain the working of any two types of inverters.

\item \iitem Explain the working of buck boost regulator.
\item Explain the role of microcontrollers in the control of power
  electronic circuits.
\ene
\Or
\item Explain the working of an isolation amplifier circuit and a
  synchronization circuit.

\markC
\ene

\newpage

\mainhead{D 30972}{2}
\semfive{NOVEMBER 2012}
\sub{\subj}
\maxtime

\partA

\iitem Given {\em two} applications of power MOSFET.
\item State the significance of power factor.
\item Name {\em two} applications of controlled rectifiers.
\item Give the classification of Choppers.
\item State the working principle of IGBT.

\markA
\partB

\item Briefly explain an application of TRIAC.
\item Explain the working principle of GTO.
\item Write a brief note on cycloconverters.
\item Explain the vector control of induction motors.
\item Explain the control of power electronic circuits using microprocessors
  with an example.
\item Define the terms load regulation and line regulation. Explain the types of UPS.

\markB
\partC

\item \iitem Explain the working of SCR with its characteristics.
\Or
\item \iitem Explain the working of power MOSFET.

\newpage \again

\item Explain the working of IGBT.
\ene
\ene

\item \iitem Explain the working of three phase converter circuit. Explain a method for
  power factor improvement.
\Or
\item Explain the method of AC voltage controller circuits.
\ene

\item \iitem Explain the working of DC chopper.
\Or
\item Explain the working of current source inverters.
\ene

\item \iitem Explain the working of switched mode power supply.
\Or
\item \iitem Explain the need for synchronization circuits.
\item Explain a simple drive circuit using power BJT.
\ene
\ene

\markC
\ene
