%
% This file is part of Calicut University Question Paper Collection.
%
% Copyright (c) 2012-2015 Mohammed Sadik P. K. <sadiq (at) sadiqpk (d0t) org>.
% License: GNU GPLv3 or later
%
% Calicut University Question Paper Collection is free software: you can
% redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation, either version 3 of the License, or
% (at your option) any later version.
% 
% Calicut University Question Paper Collection is distributed in the hope
% that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
% 
% You should have received a copy of the GNU General Public License
% along with Calicut University Question Paper Collection.
% If not, see <http://www.gnu.org/licenses/>.
% 
%

\def \subj{AI 09 506---TRANSDUCERS}

\mainhead{D 50631}{2}
\semfive{NOVEMBER 2013}
\sub{\subj}
\maxtime

\partA

\iitem What is the need for transducers?
\item State the principle of thermistor.
\item What are damping devices?
\item What is an analytical balance?
\item State the advantage of digital accelerometers over analog
  accelerometers.

\markA
\partB

\item Explain the classification of transducers.
\item Explain the working of an ionization transducer.
\item Explain the working of a capacitive transducer.
\item Explain a method to measure displacement of a body.
\item Explain the working of a consistency meter.
\item Explain the working of a bonded strain gauge.

\markB
\partC

\item \iitem Explain the working of:
\iitem Hot wire anemometer.
\item Resistive magnetic flux transducer \ene
\Or

\newpage \again

\item Explain the working of:
\iitem Strain gauge.
\item Resistive optical radiation transducer. \ene
\ene

\item \iitem Explain the working of an LVDT. Discuss its
  characteristics.
\Or
\item \iitem Discuss on Hall-effect.
\item Explain the working of a piezo electric transducer. \ene
\ene

\item \iitem Explain a method to measure torque and a method to measure
  velocity of a body.
\Or
\item Explain a method to measure force and a method to measure
  acceleration
\ene

\item \iitem Explain the working of a rotometer type viscometer.
\Or
\item Explain the working of a digital pH meter.
\ene

\markC
\ene

\newpage

\mainhead{D 30973}{2}
\semfive{OCTOBER 2012}
\sub{\subj}
\maxtime

\partA

\iitem What are passive transducers?
\item Give \emph{four} examples for active transducers.
\item State the principle of capacitive transducers.
\item Give \emph{two} advantages of digital transducers over analog 
  transducers.
\item What are load cells?
\item What is a dynamometer?
\item What is a strain gauge?
\item What is the basic of a pH meter?

\markA
\partB

\item Explain the working of a  resistive magnetic flux transducer.
\item Explain the working of a resistance thermometer.
\item Explain the working of a thermoelectric transducer.
\item Explain the working of Bourdon tubes.
\item Explain a method to measure velocity of a body.
\item Explain the working of consistency meter.

\markB

\newpage \again

\partC

\item \iitem Explain the working of a resistive optical radiation
  transducer.
\Or
\item Explain the working of hot wire anemometer and thermistor.
\ene

\item \iitem Explain the working of piezoelectric and photoelectric transducers.
\Or
\item Explain the working of LVDT and discuss its characteristics.
\ene

\item \iitem Explain a method to measure acceleration of a body. 
\Or
\item Explain the working of any \emph{one} type of dynamometer.
\ene

\item \iitem Explain the working of a digital accelerometer.
\Or
\item Explain the working of rotometer type viscometer.
\ene

\markC
\ene

\newpage

\mainhead{D 20922}{2}
\semfive{OCTOBER 2011}
\sub{\subj}
\maxtime

\partA

\iitem What are primary and secondary transducers?
\item What is Hall effect?
\item Define Gauge factor.
\item What is a dynamometer?
\item What is the function of consistency meter?

\markA
\partB

\item Explain the principle and working of thermistor.
\item Explain the working of Thermoelectric Transducer.
\item Explain any one method to measure displacement of a body.
\item Write brief notes on load cells.
\item Explain the working of bonded Strain Gauge.
\item Explain the working of Saybolt's viscometer.

\markB
\partC

\item \iitem Explain the working of the following:
\iitem Potentiometer.
\item Resistive optical Radiation transducer.
\ene
\Or

\newpage \again

\item Explain the working of:
\iitem Hot wire anemometer.
\item Resistive magnetic flux transducer.
\ene\ene

\item \iitem Explain the working of LVDT along with its characteristics.
\Or
\item Explain the working of a capacitive and piezoelectric transducer.
\ene

\item \iitem Explain a method each to measure velocity and acceleration of a body.
\Or
\item Explain a method to measure force and torque.
\ene

\item \iitem Explain a method to measure vibration of body and discuss its vibration characteristics.
\Or
\item Explain the working of a digital pH meter.
\ene

\markC
\ene
