%
% This file is part of Calicut University Question Paper Collection.
%
% Copyright (c) 2012-2015 Mohammed Sadik P. K. <sadiq (at) sadiqpk (d0t) org>.
% License: GNU GPLv3 or later
%
% Calicut University Question Paper Collection is free software: you can
% redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation, either version 3 of the License, or
% (at your option) any later version.
% 
% Calicut University Question Paper Collection is distributed in the hope
% that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
% 
% You should have received a copy of the GNU General Public License
% along with Calicut University Question Paper Collection.
% If not, see <http://www.gnu.org/licenses/>.
% 
%
\def \subj{AI 09 701---PROCESS CONTROL INSTRUMENTATION}


\mainhead{D 50563}{2}

\semseven{NOVEMBER 2013}

\sub{\subj}

\maxtime


\partA


\iitem Define degrees of freedom.
\item Draw the feed forward control of a heat exchanger.
\item List out the drawbacks of cascade control.
\item What are decouplers?
\item What are the general rules for installation of a PLC?

\markA
\partB

\item Draw the time response of a second order under damped system when subjected to unit
  step input and define peak overshoot and settling time.
\item Explain the principle of a pneumatic actuator.
\item List out the merits and drawbacks of feedback control.
\item Give two examples of adaptive control and inferential control schemes.
\item List out the relationship between time domain and frequency domain.
\item What are factors to be considered in the selection of PLCs?

\markB
\partC

\item \iitem Explain in detail various types of relays.
\Or

\newpage

\again
\item \iitem Derive time response of a first order system to unit step input. \marko{6}
\item State principle characteristics of a first order process. \marko{4}

\ene
\ene

\item \iitem Explain split range control with suitable example.
\Or
\item \iitem Explain the characteristics of a control valve. \marko{6}
\item Write short notes on cavitation. \marko{4}

\ene
\ene

\item \iitem Explain the interaction among control loops of a flash drum and
  distillation column.
\Or
\item \iitem What are the steps that constitute to basis for experimental
  identification process?
\item What is meant by offline and online process identification?

\ene
\ene


\item \iitem Explain in detail about timers and counters of a PLC?
\Or
\item \iitem What is a ladder diagram? What are its symbols? \marko{4}
\item Design a PID controller on a PLC. \marko{6}
\ene
\ene

\markC

\ene


\newpage


\mainhead{29760}{2}

\semseven{OCTOBER 2012}

\sub{\subj}

\maxtime


\partA


\iitem What is a final control element?

\item How can the power of a pneumatic actuator be increased?

\item Define C$_v$ factor of a control valve.

\item List out the merits of PLC over conventional electromagnetic relays.

\item What is controllability?


\markA

\partB


\item Differentiate between interacting and non-interacting systems with suitable examples.

\item Explain in detail about valve sizing.

\item Write short notes on adaptive control.

\item What are the methods to reduce noise in control valve?

\item What is event sequencing?

\item What is a micro-PLC?


\markB

\partCo


\item \iitem  Explain in detail about I/P and P/I converters.

\Or

\item Explain in detail about batch and continues process with suitable examples.

\ene

\newpage
\again
\item \iitem Explain in detial about cascade and feed-forward control.

\Or

\item Explain in detail about the different types of control valves industries.

\ene

\item \iitem Write short notes on step testing and pulse testing.

\Or 

\item Explain the method of examining the stability of a multivariable system.

\ene

\item \iitem Explain the functional blocks of a Programmable Logic Controller with a neat block
  diagram.

\Or

\item How can PID control be achieved using a PLC?

\ene

\ene
