%
% This file is part of Calicut University Question Paper Collection.
%
% Copyright (c) 2012-2015 Mohammed Sadik P. K. <sadiq (at) sadiqpk (d0t) org>.
% License: GNU GPLv3 or later
%
% Calicut University Question Paper Collection is free software: you can
% redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation, either version 3 of the License, or
% (at your option) any later version.
% 
% Calicut University Question Paper Collection is distributed in the hope
% that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
% 
% You should have received a copy of the GNU General Public License
% along with Calicut University Question Paper Collection.
% If not, see <http://www.gnu.org/licenses/>.
% 
%
\def \subj{ AI 09 702---ADVANCED INSTRUMENTATION}


\mainhead{D 50564}{2}

\semseven{NOVEMBER 2013}

\sub{\subj}

\maxtime


\partA


\iitem State the principle of a Wet bulb psychrometer.

\item State the principle of working of a dew point meter.

\item State the significance of quality factor of a coil.

\item What is a buffer circuit?

\item State \emph{two} features of $\text{MX}\text{I}$ bus.

\markA

\partB


\item Explain the working of wire electrode type hygrometer.

\item Write notes on smart sensors.

\item Explain the measurement of peak frequency of a signal.

\item Explain the working of aut-zero circuit.

\item Write notes on electromagnetic interference in instrumentation.

\item Explain on VME extensions for instrumentation.

\markB

\partC

\item \iitem Explain a method to measure density of liquids.

\Or

\item Explain about:
  \iitem Semiconductor sensors.
  \newpage \again
  \item MEMS.
  \ene
\ene

\item \iitem Explain a method to measure capacitance of a 
  capacitor.

\Or

\item Explain a method to measure time interval between
  \emph{two} events.
\ene

\item \iitem \iitem Write notes on Noise sources.
  \item Explain an analog to digital conversion ciruit.
  \ene

\Or

\item Explain the architecture of a virtual instrument.
  Explain an application of virtual instrumentation.
\ene

\item \iitem Explain the following interfaces:
  \iitem RS 232 C
  \item RS 485 A
  \ene

\Or

\item Write notes on:
  \iitem USB
  \item GPIB
  \ene
\ene

\markC

\ene

\newpage


\mainhead{29761}{2}

\semseven{OCTOBER 2012}

\sub{\subj}

\maxtime


\partA


\iitem What is a due cell?

\item What is MEMS?

\item State the principle of measuring Q of a ringing circuit.

\item State the principle of working of dual slot ADC.

\item State two features of MXIbus.


\markA

\partB


\item Explain the working of electrolysis type hygrometer.

\item Write notes on semiconductor sensors.

\item Explain a method to measure capacitance.

\item Write notes on noise in instrumentation systems.

\item Explain the application of virtual instrumentation system.

\item Write notes on RS 485 A standard.


\markB

\partC


\item \iitem Explain the working of a dew pointer meter.

\Or

\newpage
\again


\item Write notes on 

\iitem Film sensors

\item Nano sensors

\ene
\ene

\item \iitem Explain a digital method to measure ratio of two frequencies.

\Or

\item Explain a digital method to measure periodic time of a signal.

\ene


\item \iitem Explain the working of successive approximation ADC.

\Or

\item Explain about virtual instrumentation

\ene


\item \iitem Explain the following:-

\iitem RS 232 C

\item RS 422 A

\ene \Or

\item Explain the following:-

\iitem GPIB

\item VISA

\ene
\ene
\ene


