%
% This file is part of Calicut University Question Paper Collection.
%
% Copyright (c) 2012-2015 Mohammed Sadik P. K. <sadiq (at) sadiqpk (d0t) org>.
% License: GNU GPLv3 or later
%
% Calicut University Question Paper Collection is free software: you can
% redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation, either version 3 of the License, or
% (at your option) any later version.
% 
% Calicut University Question Paper Collection is distributed in the hope
% that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
% 
% You should have received a copy of the GNU General Public License
% along with Calicut University Question Paper Collection.
% If not, see <http://www.gnu.org/licenses/>.
% 
%
\def \subj{ AI 09 703---ELECTRONIC COMMUNICATION SYSTEMS}


\mainhead{29762}{2}

\semseven{OCTOBER 2012}

\sub{\subj}

\maxtime


\partA

\iitem What are the frequency ranges for AM and FM broadcasting?

\item Define SWR.

\item State sampling theorem.

\item What is WDM?

\item Define co-channel interference.


\markA

\partB


\item Briefly explain the various types of Transmission Lines.

\item What is the need of modulation? Explain.

\item Explain the generation of PWM.

\item Explain Slope Overload Noise and Granular Noise.

\item Compare PCM and DM.

\item With functional block diagram explain Telemetry.


\markB

\partCo


\item \iitem Derive an expression for amplitude modulated wave and its power relation.

\Or

\item Derive an expression for Frequency Modulated wave and compare it with
      Phase Modulated wave expression.

\ene

\newpage
\again

\item \iitem With block diagram explain the operation of a Super Heterodyne reciever and 
  list its advantages over Tuned Radio Frequency receiver.

\Or

\item \iitem Explain the operation of a Coherent Detector.

\item Explain the geenration and detection of PPM.

\ene
\ene

\item \iitem With block diagram explain digital communication system.

\Or

\item Explain in detail about 

\iitem ASK and 
\item FSK

\ene
\ene

\item \iitem With block diagram explain the earth station and transponder of a 
  satellite communication system.

\Or

\item \iitem Explain the advantage of Fiber Optical Communication.

\item Derive an expression for Co-channel reuse ratio of a Cellular communication.

\ene
\ene
\markC
\ene
