%
% This file is part of Calicut University Question Paper Collection.
%
% Copyright (c) 2012-2015 Mohammed Sadik P. K. <sadiq (at) sadiqpk (d0t) org>.
% License: GNU GPLv3 or later
%
% Calicut University Question Paper Collection is free software: you can
% redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation, either version 3 of the License, or
% (at your option) any later version.
% 
% Calicut University Question Paper Collection is distributed in the hope
% that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
% 
% You should have received a copy of the GNU General Public License
% along with Calicut University Question Paper Collection.
% If not, see <http://www.gnu.org/licenses/>.
% 
%
\def \subj{EC/PTEC 09 803 L23---DATA STRUCTURES AND ALGORITHMS}


\mainhead{C 60558}{2}
\semeight{APRIL 2014}
\sub{\subj}
\maxtime

\partA

\iitem What is a priority queue?
\item What is the use of head nodes in the linked lists?
\item Define Digraph.
\item State the principle of radix sort.
\item State \emph{two} principles of programming.

\markA
\partB

\item Write an algorithm to find the address of the element A($i, j$), $i \geq j$,
  when lower triangular matrix of A is represented sequentially.
\item Show how $n$($\geq 3$) stacks can be implemented in one array.
\item Write an algorithm to reverse the direction of the links of a singly linked list.
\item Explain the preorder of a binary tree.
\item Explain any \emph{one} external sorting method.
\item Explain recursive function with an example.

\markB
\partC

\item \iitem Write programs to convert a postfix expression to infix, a prefix expression
  to postfix.
\Or

\newpage \again

\item A data presentation maps two stacks into an one dimensional array so that the elements
  of first stack are stored at odd index values and the elements of other stack are stored at
  even index values. Write algorithms to add and delete elements from these stacks.
\ene

\item \iitem Write algorithms to implement, add and delete items from a doubly linked list.
\Or
\item Write an algorithm to check two expressions are identical.
\ene

\item \iitem Write an algorithm for breadth first search of items.
\Or
\item Write an algorithm to implement Merge sorting of $n$ numbers.
\ene

\item \iitem Explain system life cycle.
\Or
\item Explain about time and space complexity of algorithms.
\ene

\markC
\ene

\newpage

\mainhead{C 41652}{2}
\semeight{APRIL 2013}
\sub{\subj}
\maxtime

\partA

\iitem What is a sparse matrix?
\item Define a circular queue.
\item Name two applications for linked lists.
\item Define Digraph. Given an application for.
\item What is meant by system life-cycle?

\markA
\partB

\item Explain the array implementation of a stack.
\item Write a procedure to delete a mode from a doubly
  linked circular list.
\item Write an algorithm to sort a given set of numbers in 
  ascending order using bubble sort procedure.
\item Explain the linear and linked representation of a binary tree.
\item Write briefly on principles of programming.
\item A square matrix is said to be an upper triangular matrix when all
  the elements below the main diagonal qre zero. Write an algorithm to find
  the address of the element A$ (i, j), i\leq j,$ when the upper triangular
  matrix is represented sequentially.

\markB
\partCo

\item \iitem Write an algorithm to compute the product of the two
  sparse matrices A and B.
\Or

\newpage \again

\item Represent a Deque in an array. Write algorithms to add an 
  element at the end of a deque.
\ene

\item \iitem \iitem Write a program that reads the name, age and salary of 10 persons
  and maintains them in linked list sorted by name.
\item Compare the advantages and disadvantages of arrays over linked lists.
\ene
\Or
\item Write a program to convert an infix arithmetic expression into a postfix
  arithmetic expression. Use expression Q: (A-B) * (C/D) + E. Show in tabular form
  the changing status of stack.
\ene

\item \iitem Write depth first search algorithm for the traversal of any graph.
  Explain the time complexity of the algorithm.
\Or
\item Write programs to:
\iitem Swap a binary tree.
\item Compute the internal path length of a binary tree.
\ene\ene

\item \iitem Explain the system life-cycle.
\Or
\item Explain about performance analysis of algorithm.
\ene

\markC
\ene

