%
% This file is part of Calicut University Question Paper Collection.
%
% Copyright (c) 2012-2015 Mohammed Sadik P. K. <sadiq (at) sadiqpk (d0t) org>.
% License: GNU GPLv3 or later
%
% Calicut University Question Paper Collection is free software: you can
% redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation, either version 3 of the License, or
% (at your option) any later version.
% 
% Calicut University Question Paper Collection is distributed in the hope
% that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
% 
% You should have received a copy of the GNU General Public License
% along with Calicut University Question Paper Collection.
% If not, see <http://www.gnu.org/licenses/>.
% 
%
\def \subj{AI 09 804 L09---ADVANCED BIOMEDICAL INSTRUMENTATION}

\mainhead{C 60502}{2}
\semeight{APRIL 2014}
\sub{\subj}
\maxtime

\partA

\iitem Distinguish between nuclear fission and nuclear fusion.
\item State the principle of NMR imaging.
\item What is macro-shock?
\item Name the components of a drug infusion system.
\item List out the properties of a Huffman Code.

\markA
\partB

\item Mention the biological effects of NMR imaging.
\item Define the terms coagulation and blending.
\item List out the functions of Kidneys.
\item Explain the principle of a Geiger Mullar Counter.
\item What are incubators?
\item Write short notes on a signal averaging.

\markB
\partC

\item \iitem Describe in detail about the working principle of a Gamma Camera
  with a neat block diagram.
\Or

\newpage \again

\item Discuss in detail about the image reconstruction techniques employed in
  NMR imaging.
\ene

\item \iitem Explain the working principle of an Ultrasonic therapy unit with a
  neat sketch.
\Or
\item Explain in detail about working principle of a Hemo-dialyser.
\ene

\item \iitem Explain the working principle of an Lithotripsy unit with a neat
  block diagram.
\Or
\item Describe in detail about functioning of Pressure Cycled Ventilator.
\ene

\item \iitem Explain in detail about working of a portable arrhythmia monitor.
\Or
\item Discuss in detail about any \emph{two} data reduction techniques.
\ene

\markC
\ene

