%
% This file is part of Calicut University Question Paper Collection.
%
% Copyright (c) 2012-2015 Mohammed Sadik P. K. <sadiq (at) sadiqpk (d0t) org>.
% License: GNU GPLv3 or later
%
% Calicut University Question Paper Collection is free software: you can
% redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation, either version 3 of the License, or
% (at your option) any later version.
% 
% Calicut University Question Paper Collection is distributed in the hope
% that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
% 
% You should have received a copy of the GNU General Public License
% along with Calicut University Question Paper Collection.
% If not, see <http://www.gnu.org/licenses/>.
% 
%
\def \subj{AI 09 801---ANALYTICAL AND OPTO-ELECTRONIC INSTRUMENTATION}

\mainhead{C 80507}{2}

\semeight{APRIL 2015}

\sub{\subj}

\maxtime

\partA

\iitem What is the function of filters in spectro photometry?
\item Define chromatography.
\item Explain the principle of polarization.
\item Define interference.
\item What is the principle of optic fibre?

\markA
\partB

\item Write brief note on FTIR.
\item Explain nuclear magnetic resonance spectrometry.
\item Explain the principle of gras analyzer.
\item Write a note on a single beam photometer.
\item Explain the construction fo a hologram.
\item Write a brief note on losses in optical fibre.

\markB
\partC

\item \iitem Explain the principle and working of infrared spectro photometer.
\Or
\item Discuss in detail about flame emission and atmoic absorption spectrometry.
\ene

\newpage \again

\item \iitem With the aid of necessary diagrams explain the principle and
  instrumentation of Raman spectrometry.
\Or
\item Explain different types of mass spectrometry.
\ene

\item \iitem Explain the working of a semiconductor laser.
\Or
\item Explain the working of Jamin and Mach-Zehndel interferometer.
\ene

\item \iitem With refractive index profile explain step index single mode and step
  index multimode fibre.
\Or
\item \iitem Write briefly about optice fibre fabrication.
  \item Explain various properties of optic fibre.
  \ene
\ene
\markC
\ene

\newpage

\mainhead{C 60500}{2}

\semeight{APRIL 2014}

\sub{\subj}

\maxtime

\partA

\iitem What is the role of a filter?
\item State the principle of a chromatograph.
\item What is population inversion?
\item Name the losses in an optical fibre.
\item List out the advantages of light emitting diodes.

\markA
\partB

\item Differentiate between Single beam and Double beam photometers.
\item How will you measure smoke and dust?
\item What are optocouplers?
\item Mention the properties of LASER.
\item List out the applications of holography.
\item Differentiate between Step index and Graded index fibers.

\markB
\partC

\item \iitem Describe in detail about various radiation sources and detectors.
\Or
\item Discuss in detail about the working principle of ultraviolet
  spectro-photometer.
\ene

\newpage \again

\item \iitem Explain the working principle of X-ray Spectro-photometer with a neat
  sketch.
\Or
\item Explain in detail about working principle of a thermal conductivity type
  gas analyzer.
\ene

\item \iitem Explain the working principle of a Semiconductor type LASER.
\Or
\item Describe in detail about Avalanche photodiode and PIN photodiode detectors.
\ene

\item \iitem Explain in detail about holographic interferometry.
\Or
\item Discuss in detail about fibre optic sensors for measuring temperature and
  liquid level.
\ene
\markC
\ene

\newpage

\mainhead{41594}{2}

\semeight{APRIL 2013}

\sub{\subj}

\maxtime


\partA


\iitem Define spectrophotometry.

\item What is meant by FTIR.

\item Define spectrometer.

\item Define population inversion.

\item What is meant by optical telemetry.


\markA
\partB


\item Explain atomic emission spectrometry.

\item Explain the general principle of chromatography.

\item Explain the working of avalanche photodiode.

\item Explain the principle of operation of Fabry-Perot interferometer.

\item Explain any \emph{two} types of fiber optic sensors.

\item Explain the principle of holography and its applications.


\markB
\partC


\item \iitem Explain in detail about different ultraviolet spectrophotometer.

\Or

\item Explain different types of photometers.

\ene

\item \iitem Briefly explain the principle and working of ESR spectrometer.

\Or

\item Explain different types of gas analyzers in detail.

\ene

\item \iitem Briefly explain constructional features of liquid crystal display.

\Or

\item What is meant by modulation? Discuss the operation of magneto optic modulator.

\ene

\item \iitem Explain the propagation mechanism in step index and graded index fiber.

\Or

\item Explain the measurement of optic fiber characteristics.

\ene

\markC
\ene
