%
% This file is part of Calicut University Question Paper Collection.
%
% Copyright (c) 2012-2015 Mohammed Sadik P. K. <sadiq (at) sadiqpk (d0t) org>.
% License: GNU GPLv3 or later
%
% Calicut University Question Paper Collection is free software: you can
% redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation, either version 3 of the License, or
% (at your option) any later version.
% 
% Calicut University Question Paper Collection is distributed in the hope
% that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
% 
% You should have received a copy of the GNU General Public License
% along with Calicut University Question Paper Collection.
% If not, see <http://www.gnu.org/licenses/>.
% 
%
\def \subj{EN09 301---ENGINEERING MATHEMATICS---III}

\mainhead{D 51010}{2}
\semthree{OCTOBER 2013}
\sub{\subj}
\maxtime

\partA

\iitem Define Harmonic functions.
\item Find the image of the circle $|z| = a$ under the transformation
  $w = (3 + 4i)z$.
\item State Cauchy's integral formula.
\item Show that the intersection of any two subspaces U and W of a
  vector space V is also a subspace.
\item Find the Fourier Cosine transform of $e^{-ax} (a>0)$.

\markA
\partB

\item Find the analytic function $w = u +iv$, if $v = e^{-x} (x\cos
  y + y \sin y)$. Hence find $u$.
\item Find the image of the semi-infinite strip $0 \leq x \leq \pi, y \geq 0$
  under the transformation $w = \cos z$.
\item Find the residues at the isolated singularities of the function
  $\dfrac{z^2}{z^2 + a^2}$.
\item Determine whether the vectors $(2, 1, 1)$, $(5, 2, 1)$ and $(4, 3, 5)$
  form a basis for the vector space $\mathbb{R}^3$.
\item Find the Fourier transform of $f(x)$ if
$f(x) =
\begin{cases}
1, & \, |x| < a\\
0, & \, |x| > a > 0
\end{cases}$.
Hence deduce that
\iitem $\int\limits_0^\infty \dfrac{\sin t}{t} dt = \dfrac{\pi}{2}$
\item $\int\limits_0^\infty \left(\dfrac{\sin t}{t}\right)^2 dt = \dfrac{\pi}{2}$
\ene
\item Show that any set of \emph{three} vectors in $\mathbb{R}^2$ is linearly
  dependent.

\markB

\newpage \again

\partC

\item \iitem If $f(z) = \sqrt{|xy|}$, prove that $f(z)$ satisfies Cauchy-Riemann
  equations at the origin but it is not analytic at the origin.
\Or
\item Prove that $w = \dfrac{z}{1 - z}$ maps the upper half of the $z$-plane
  onto the upper half of the $w$-plane. What is the image of the circle
  $|z| = 1$ under this transformation?
\ene

\item \iitem Obtain Laurent's expansion for $f(z) = \dfrac{1}{(z - 1)(z - 2)}$
  valid in the regions:
\iitem $|z - 1| < 1$.
\item $|z| > 2$. \ene
\Or
\item Using Contour integration show that
\[ \int\limits_0^{2\pi} \dfrac{\cos 3\theta}{5 - 4\cos\theta} d\theta = \dfrac{\pi}{12}\]
\ene

\item \iitem Let U and W be the subspaces of $\mathbb{R}^4$ generated by \{$(1, 1, 0,
  -1)$, $(1, 2, 3, 0)$, $(2, 3, 3, -1)$\} and \{$(1, 2, 2, -2)$, $(2, 3, 2, -3)$,
  $(1, 3, 4, -3)$\} respectively, find
\iitem dim (U$+$W). \item dim (U$\cap$W).\ene
\Or
\item Verify that the vectors $\left\lgroup\dfrac{1}{3}, \dfrac{2}{3},
  \dfrac{2}{3}\right\rgroup\!\!,$ $\left\lgroup\dfrac{2}{3}, \dfrac{1}{3},
  \dfrac{2}{3}\right\rgroup$ and $\left\lgroup\dfrac{2}{3}, \dfrac{2}{3},
  \dfrac{1}{3}\right\rgroup$ form an orthonormal basis for V$_3$(R) relative to the
  standard inner product.
\ene

\item \iitem If F$[f(x)] = \bar{f}(s)$, then show that F$[f(ax)] = \dfrac {1}{|a|}
  \bar{f}\left\lgroup\dfrac{s}{a}\right\rgroup\!\!$.
\Or
\item Find the Fourier sine transform of $e^{-ax} (a>0)$. Hence find F$_s\{
  xe^{-ax}\}$ and F$_s\left\{\dfrac{e^{-ax}}{x}\right\}$.
\ene

\markC
\ene

\newpage

\mainhead{D 30886}{2}
\semthree{OCTOBER 2012}
\sub{\subj}
\maxtime

\partA

\iitem Determine constant `$a$' such that $u = e^{ax}\cos 3y$ is harmonic.
\item Discus the nature and location of singularities of the function
  $f(z) = \dfrac{\tan z}{z}$.
\item Find the critical points if any of the mapping W $= \sin z$.
\item Show that the set of all $2 \times 2$ non-singular matrices is not
  a vector space.

\item Find the Fourier transform of the function
  $f(t) = 
  \begin{cases}
    5, & \, -2 \leq t \leq  2\\
    0, & \, \text{otherwise}\\
  \end{cases}$

\markA
\partB

\item Show that $|z|^2$ is not analytic at any point.
\item Evaluate $\int\limits_0^{2+i} (\bar{z})^2dz$ along the line
  $y = \dfrac{x}{2}$.
\item Find the Fourier sine transform of $3e^{-2x} + 2e^{-3x}$.
\item If F$(s)$ is the Fourier transform $f(x)$, then show that
  F$\{f(ax)\} = \dfrac{1}{a} \text{F}\left(\dfrac{S}{a}\right)$.
\item is U$_1$ = $\begin{bmatrix} 1\\ 1\\ 1 \end{bmatrix} $,
  U$_2$ = $\begin{bmatrix} 1\\ 2\\ 3 \end{bmatrix} $,
  U$_3$ = $\begin{bmatrix} 2\\ -1\\ 1 \end{bmatrix} $
  a basis of $\mathbb{R}^3$.
\item If W be a proper sub-space of a finite dimensional vector space
  V, then show that W is finite dimensional and dim W $\leq$ dim V.

\markB

\newpage \again

\partC

\item \iitem Determine the analytic function $f(z) = u + i\text{V}$, where
  $u + \text{V} = (x - y) (x^2 + 4xy + y^2)$.
\Or
\item Find the image of the first quadrant $x > 0$, $y > 0$ under
W = $\dfrac {z-i}{z+i}$.
\ene

\item \iitem \iitem Find the Laurent's series expansion of
  $\dfrac{e^{2z}}{(z-1)^3}$ about the singularity of $z = 1$.
\item Evaluate $\int\limits_C \dfrac{dz}{z^2 + 4)^2}$; C is $|z - i| = 2$.
\ene
\Or
\item Evaluate $\int\limits_{-\infty}^{\infty} \dfrac{x^2 dx}{(x^2 + 1) (x^2 + 4)}$.
\ene

\item \iitem Find a basis and the dimension of the subspace W of $\mathbb{R}^4$
  generated by $(1, -4, 1, 3) (2, -1, 3, -1)$ and $(0, 2, 1, -5)$.
\Or
\item Apply Gram-Schmidth process toe the vectors $\beta_1 = (1, 0, 1)$,
  $\beta_2 = (1, 0, -1)$, $\beta_3 = (0, 3, 4)$, to obtain an
  orthonormal basis for $\mathbb{R}^3$ with the standard inner product.
\ene

\item \iitem Find the Fourier Cosine transform of $f(x) = \dfrac{1}{1 + x^2}$.
\Or
\item Express the function
$f(x) =
\begin{cases}
1, & \, \text{for } |x| \leq 1\\
0, & \, \text{for } |x| > 1
\end{cases}$
as a Fourier integral. Hence evaluate $\int\limits_0^\infty
\dfrac{\sin\lambda \cos\lambda x}{\lambda} d\lambda$
\ene

\markC
\ene

\newpage

\mainhead{D 20603}{2}
\semthree{OCTOBER 2011}
\sub{\subj}
\maxtime

\partA

\iitem Determine where the Cauchy-Riemann conditions are satisfied for the function
 $ w = xy^2 + iyx^2$.
\item Define isogonal mapping.
\item Express the residue of a function at an isolated singularity as a contour integral.
\item How do you define the linear span of a set of vectors in a vector space.
\item Write down the complex Fourier transform pair.

\markA
\partB

\item Find a function $w$ such that $w$ + $u$+ $iv$ is analytic, given that $v = 3x^2y - y^3$.
\item Find the image of the semi-infinite strip $x > 0, 0 < y < 2$ under the transformation
  $w = iz +1$. Show the regions graphically.
\item Evaluate $\int\dfrac{\sin \pi z^2 + \cos \pi z^3}{(z - 1)(z - 2)}\ud z,$ around $|z| = 3.$
\item Show that the vectors $u = (1, 2, -1), v = (2, 1, -2),$ and $w = (1, 4, 3)$ generate R$^3$.
\item Verify that the triangle inequality is satisfied by the vectors $(0, 1, 1)$ and $(1, 1, 0)$ in R$^3$.
\item Show that $f(x) = e^{-x^2/2}$ is self-reciprocal under Fourier transform.

\markB
\partC

\item \iitem Determine the analytic function $f(z) = u + iv$ if $ u - v = \dfrac{\cos x + \sin x - e^{-y}}{
  2(\cos x - \cosh y)}$, given that $f \left(\dfrac{\pi}{2}\right)=0$.
\Or
\item Find the invariant points of the transformation $w = - \dfrac{2z + 4i}{iz + 1}$, and prove that these 
  two points, together with any point $z$ and its image $w$, form a set of four points having a constant cross
  ratio. What is this cross ratio?
\ene

\item \iitem Find the Laurent series expansion of the function $f(z) = \dfrac{z^2 - 6z - 1}{(z - 1)(z - 3)(z + 2)}$
  valid in the region $3 < |z + 2| < 5.$
\Or
\item Find the value of the integral $\int\limits_{C} \dfrac{dz}{z^2 (z + 4)}$ taken counter clockwise around
  the circle (i) $|z| = 2'$, (ii) $|z + 2| = 3$.
\ene

\item \iitem Find the co-ordinates of the vector (2, 1, -6) of V$_3$(R) relative to the basis F$_1$ = (1, 1, 2),
  F$_2$ = (3, -1, 0) and F$_3$ = (2, 0, -1).
\again
\Or
\item Apply the Gram-Schmidt orthogonalisation process to obtain an orthonormal basis for $\mathrm{R}^3$ from the basis given by
  $v_1 = (3, 0, 4),\, v_2 = (-1, 0, 7),\, v_3 = (2, 9, 11)$.
\ene

\item \iitem Find the Fourier sine and cosine transforms of $f(x) = 2 e^{-5x} + 5 e^{-2x}$.
\Or
\item Find the Fourier transform of

$f(x) = 
  \begin{cases}
    2 - |x|,& \, \text{in } |x| \leq  2\\
    0, & \, \text{in } |x| \leq 2.\\
  \end{cases}$

Hence find the value of $\int\limits_0^\infty \left( \dfrac{\sin t}{t}\right)^4 dt$.
\ene

\markC
\ene

\newpage

\mainhead{D 10025}{2}
\semthree{NOVEMBER 2010}
\sub{\subj}
\maxtime

\partA

\iitem Prove that $f(z) = z \text{J}_{mx}$. is differentiable only at $z = 0$.
\item Obtain the expansion of $\dfrac{z-1}{z^2}$ in a Taylor series in powers of ($z - 1$).
\item Find the invariant points of the transformation $\omega = \dfrac{3z - 5i}{iz - 1}$.
\item Determine the subspace spanned by H = $\{(1, -2, 3), (3, 0, 1)\}$ in $\mathrm{R}^3$.
\item Find the Fourier sine transform of 

  $f(x) = 
  \begin{cases}
    1, & 0 \leq x < a\\
    0, & x \geq a
  \end{cases}$

\markA
\partB

\item Find the image of the line $y - x + 1 = 0$ under the transformation $w =\dfrac{1}{z}$.
\item Evaluate $\int\limits_c \dfrac{3z^2 + 7z + 1}{3 + 1} \ud z$ where C is the circle $|z + i| = 1$.
\item Let V = R$^4$ and W be a subspace generated by (1, -2, 5, -3), (2, 3, 1, -4) and (3, 8, -3, -5).
  Find basis and dim(W).
\item Show that the set $\{(x, y, z) \in \mathrm{R}^3 : 2x + 5y - 7z = 0\}$ is a vector subspace
  of $\mathrm{R}^3$.
\item Find the Fourier transform of the function $f(t) = e^{-a|t|}, -\infty < t < \infty, a>0.$
\item Find the Fourier cosine transform of $f(x) = \dfrac{e^{-ax}}{x}$.

\markB

\newpage \again

\partC

\item \iitem Find the bilinear transformation which maps the points z = 1, i, -1 on to the points $w$ = -i.
  Hence find the image of $|z| < 1$.
\Or
\item Determine the analytic function whose real part is $\dfrac{\sin 2x}{\cosh 2y - \cos 2x}$.
\ene

\item \iitem Evaluate $\displaystyle\oint\limits_C \dfrac{e^z \ud z}{\cos \pi z}$ where C is
  the unit circle $|z| = 1$.
\Or
\item Evaluate $\displaystyle \int\limits_0^{2\pi} \dfrac{\ud \theta}{5 - 3 \cos \theta}$.
\ene

\item \iitem Let $u_1 = (1, 0, 0), u_2 = (-3, 4, 0)$ and $u_3 = (3, -6, 3)$.
\iitem Show that B $= \{u_1, u_2, u_3\}$ is a basis of $\mathrm{R}^3$.
\item Find the co-ordinate vector for $v = (-8, 2, 3).$
\ene 
\Or
\item Find the orthonormal basis for the subspace spanned by (1, 2, 1), (1, 0, 1), (3, 1, 0) of $\mathrm{R}^3$.
\ene

\item \iitem Using the Fourier Integral representation, show that $\displaystyle \int\limits_0^\infty
  \dfrac{w \sin x w}{1 + w} \ud w = \dfrac{\pi}{2} e^{-x}, (x>0).$
\Or
\item Show that the Fourier transform of $e^{{-x^2}/2}$ is self reciprocal. 
\ene

\markC
\ene
