%
% This file is part of Calicut University Question Paper Collection.
%
% Copyright (c) 2012-2015 Mohammed Sadik P. K. <sadiq (at) sadiqpk (d0t) org>.
% License: GNU GPLv3 or later
%
% Calicut University Question Paper Collection is free software: you can
% redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation, either version 3 of the License, or
% (at your option) any later version.
% 
% Calicut University Question Paper Collection is distributed in the hope
% that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
% 
% You should have received a copy of the GNU General Public License
% along with Calicut University Question Paper Collection.
% If not, see <http://www.gnu.org/licenses/>.
% 
%
\def \subj{EN09 302---HUMANITIES AND COMMUNICATION SKILLS}

\mainhead{D 20604}{2}
\semthree{OCTOBER 2011}
\sub{\subj}
\maxtime

\partA

\iitem What is the role of a topic sentence in a paragraph?
\item Explain the term Communication Barriers.
\item State the source of Technology in the Indian context.
\item Distinguish between Culture and Civilization.
\item Point out the role of science in Egyptian culture.

\markA
\partB

\item Write a note on nature and importance of group discussion.
\item What are the different types of listening?
\item Rewrite the following sentences effectively:
\iitem I want a boy with no drinks. If he wants he can wear jeans in house but while stepping
  out of house he should give respect to our caste.
\item Exclusive dedication to necessitous chores without interludes of hedonistic diversion renders
  Jack a hebetudinous fellow.
\ene
\item Explain briefly the Industries in Greek culture.
\item What is the cause for Industrial Revolution?
\item What are the culture impact for communication revolution?

\markB

\newpage \again

\partC

\item \iitem Rewrite the following effectively making necessary changes:
\iitem Trains travel more faster today than they did ten years ago.
\item Nobody in the office could not give me the correct directions for getting the refund.
\item How much it costs?
\item Our major source of energy is the oil.
\item I have been trying to place him under contract for three years.
\item The department sent their representatives to the meeting.
\item After they had eaten the children left the canteen.
\item They tried to put out the fire which was destroying the building
  without success.
\item The man aimed a blow at my head which slipped off on my shoulders.
\item This lack of complete information, data and details, is present throughout the report
  and can be seen as one goes through it.
\ene
\Or
\item Write a paragraph in about 200 words on the following topic: `Social service should be made
  compulsory in Professional colleges.'
\ene

\item \iitem Read the following passage and highlight the data contained in it in a suitable non-verbal
  medium so that the essential information is read easily and immediately.\\
  
  \begin{tabular}{p{\textwidth- 2cm}}
    
    Thanks to the economic liberalization a number of foreign car manufacturers have set shops in India.
    The Indian car manufacturers also have increased their capacity. As a result the production and sales
    of passenger cars have shown a phenomenal increase in the last few years and it is going up further.

    The production of premier cars, i.e. car priced above 6 lakhs of them will be sold in India and the
    rest are expected to be sold abroad. For the Indian car users. i.e. Rs 3 lakhs will continue to be
    the one within the reach. In the year 2001, 5.3 lakh `small' cars will be produced
    and 4.5 lakhs will be sold in the country. Between this two comes the medium
    category cars priced between Rs 3 lakhs and Rs 6 lakhs. In this category 4 lakhs will
    be produced in the year 2001
    and one-third of them will be sold in India. The remaining cars are meant to be exported.

    Thus in the year 2001 a total number of 16.6 lakh cars will be manufactured in India and of them
    7.1 lakh will be sold in our country.
    
  \end{tabular}
\Or
\item We are reputed IT company looking for software professionals for our development centre at
  Mumbai. As a software engineer you must have 1 to 4 years of experience in IT organization, 
  MCA/Engineering graduates with extensive experience to design, development and testing will be 
  preferred. Please send your detailed CV to Wise Tech. Solutions, Wina A Level II, Tower-1, Cyber
  City, New Delhi - 110 030.
\ene

\item \iitem Discuss the impact of Science and Technology in the development of modern civilization.
\Or
\item Describe the contribution of Chinese culture to the world.
\ene

\item \iitem State and explain the methods behind art of dealing with people.
\Or
\item What is meant by social responsibility? Discuss the social responsibility of Engineers 
  to the society.
\ene

\markC
\ene

\newpage

\mainhead{10026}{2}
\semthree{DECEMBER 2010}
\sub{\subj}
\maxtime

\partA

\iitem What is the importance of Stone Age to the students of technology?
\item Define communication.
\item How is a short report different from a long one?
\item What is skimming?
\item What is professional ethics?

\markA
\partB

\item Write a note on the Egyptian contribution to civil engineering.
\item What are the different reading skills?
\item Define body language and its role in communication.
\item What is the difference between note making and note taking?
\item What is CV? Why is it relevant in an interview?
\item What is code of ethics? How does it helps engineers?

\markB
\partC

\item \iitem Discuss India's development in the field of information technology.
\Or
\item Discuss the impact of space science on Indian technology.
\ene

\newpage \again

\item \iitem What are the points to be remembered to make a group discussion effective?
\Or
\item What are the barriers to communication? Explain using a model.
\ene

\item \iitem Make a report of an industrial accident or a natural disaster you are familiar with.
\Or
\item You purpose to start an industry. Make a project report of the same.
\ene

\item \iitem What is cyber crime? Explain with examples.
\Or
\item Discuss environmental ethics.
\ene

\markC
\ene



